### 2022-09-24 paper/main.tex
add paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Added packages
\usepackage{cite}  
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}

% Latex math commands
\newcommand{\Ls}{\mathcal{L}}
\def\sP{{\mathbb{P}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

%\title{SafeAMC: Adversarial training for robust modulation recognition models}

%\name{Javier Maroto\thanks{This work has been sponsored by armasuisse Science and Technology with the project ROBIN (project code Aramis 047-22).}$^{\star}$ \qquad Gérôme Bovet$^{\dagger}$ \qquad Pascal Frossard$^{\star}$}

%\address{$^{\star}$ EPFL, Switzerland \\
%  $^{\dagger}$armasuisse Science\&Technology, Cyber-Defence Campus, Switzerland}

\title{ML distillation
\thanks{This work has been sponsored by armasuisse Science and Technology with the project ARNO (project code ???).}
}

\author{\IEEEauthorblockN{Javier Maroto}
\IEEEauthorblockA{\textit{Signal Processing Laboratory (LTS4)} \\ \textit{EPFL, Switzerland}}
\and
\IEEEauthorblockN{Gérôme Bovet}
\IEEEauthorblockA{\textit{armasuisse Science\&Technology} \\
\textit{Cyber-Defence Campus, Switzerland}}
\and
\IEEEauthorblockN{Pascal Frossard}
\IEEEauthorblockA{\textit{Signal Processing Laboratory (LTS4)} \\ \textit{EPFL, Switzerland}}}

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

\begin{IEEEkeywords}
\end{IEEEkeywords}

\section{Introduction}

%

Deep learning \cite{goodfellow2016deep}

\section{Maximum likelihood}

Normally, to perform well on automatic modulation classification (AMC), neural networks are trained to infer the modulation used in transmission from the signal received. Thus, the network will be optimized to be as confident and accurate as possible on the training set. However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals this may no longer the case. The reason is that there could be a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict. In some extreme cases, the noise can even make the task impossible to solve, where the signal received could have been generated from any of multiple modulations with similar probability.

In many other tasks, these probabilities would be difficult or impossible to obtain. However, in AMC, there is an optimal method that gives us these probabilities with perfect accuracy: Maximum Likelihood (ML). Despite its optimal performance, neural networks are still preferred over ML for a simple reason: ML does not perform well when we do not have full knowledge of the channel effects on the signal. In fact, even if we were to estimate the channel, any small deviation from the real channel parameters has a major effect on the ML performance. Moreover, incorporating this uncertainty in the ML formulation makes it computationally unfeasible.

Based on these limitations, we propose a hybrid approach. We will use a neural network for inference, but we will train it with the probabilities given by maximum likelihood. This is feasible when we consider that we can have full knowledge of the channel conditions by generating the training samples ourselves. Moreover, after training the neural network, ML is no longer needed. Thus allowing our model to be usable under unknown channel conditions, which is typical in real AMC scenarios.

\section{Knowledge distillation}

\section{Experiments}

We propose to evaluate our methodology on scenarios with different levels of non-coherence. This way, we can verify if the probabilities generated by maximum likelihood in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions. 
For all the experiments the task will be the same. We will train the neural network to be able to distinguish between the following digital modulations: BPSK, QPSK, 8/16/32/64/128/256-PSK, PAM4, 16/32/64/128/256-QAM. This is consistent with other experimental settings used in the field \cite{}.  % Avoided highlighting that analog modulations are not used (not viable with our methodology, would have to be ignored)
For all settings, we use 200KHz for the sampling frequency.

For the first scenario, we consider a gaussian channel with varying levels of noise ranging from -6 to 18 dB SNR. For the transmitter, we use 8 samples per symbol and a root raised cosine filter with rolloff 0.35.

For the second scenario, we additionally vary the transmitter settings. We consider either 2, 4, 8 or 16 samples per symbol and the rolloff of the filter can range from 0.15 to 0.45.

For the third and final scenario, we use the transmitter settings of the first scenario, but we consider also Rician and Rayleigh channels with AWGN noise. % Maybe specify the parameters used in both channels...

\bibliographystyle{IEEEbib}
\bibliography{references}

\end{document}

### 2022-09-27 paper/main.tex
Paper update

@@
 
+%Adversarial perturbations
+Recent studies have highlighted security issues in DNNs models \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}.
+Specifically, those models have been shown to be vulnerable to adversarial examples, which are carefully crafted but almost imperceptible perturbations, namely adversarial perturbations, that are added to a real data sample.
+For AMC, a perturbation can be crafted by solving the following optimization:
+\begin{equation}
+\label{eq:adv_pert}
+    \delta_i^* = \argmax_{\delta_i}\Ls(f_{\theta}(x_i + \delta_i), y_i) \quad \text{s.t.} \quad \lVert \delta_i \rVert_{\infty} \leq \varepsilon
+\end{equation}
+
 \section{Maximum likelihood}
@@
 
+\begin{equation}
+    \text{ST} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), y_i)
+\end{equation}
+where $N$ is the size of the training set, $\Ls$ is the cross-entropy loss, $f_{\theta}$ is the neural network defined with weights $\theta$ and $x_i$ is the signal received.
+$y_i$ is a one-hot-encoded vector of length K, that encodes the modulation that was used to generate the signal.
+
+\begin{equation}
+    \text{ST\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), p_{ML}(r(x_i)))
+\end{equation}
+where $p_{ML}$ is the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal.
+Thus, $r$ will be dependent on the filter and samples per symbol used by the transmitter.
+For this reason, this loss function can only be used when training the network, as this information can be assumed to be known.
+
+\begin{equation}
+    \text{ST\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i), y_i)
+\end{equation}
+where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i)))$.
+This effectively filters all signals that have label noise.
+Intuitevely, those signals would be the most corrupted by the noise, to the point where it is more probable that it was generated from a modulation different than the one that was actually used, and potentially confusing the network during training.
+
+\begin{equation}
+    \text{AT} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), y_i)
+\end{equation}
+where $x_i' = x_i + \delta_i^*$ is a crafted adversarial signal that maximizes the cross-entropy loss of the neural network in the neighborhood of $x_i$.
+
+\begin{equation}
+    \text{AT\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(x_i')))
+\end{equation}
+
+\begin{equation}
+    \text{AT\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i'), y_i)
+\end{equation}
+where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i')))$.
+
+In the case where the channel is not gaussian
+\begin{equation}
+    \text{AT\_NML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(x_i))
+\end{equation}
+
+\begin{equation}
+    \text{AT\_AML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(x_i)'))
+\end{equation}
+where $r(x_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of maximum likelihood in the neighborhood of $r(x_i)$.
+
 \section{Experiments}
@@
 This way, we can verify if the probabilities generated by maximum likelihood in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions.
+
 For all the experiments the task will be the same.
-We will train the neural network to be able to distinguish between the following digital modulations: BPSK, QPSK, 8/16/32/64/128/256-PSK, PAM4, 16/32/64/128/256-QAM.
+We will train the neural network to be able to distinguish between the following digital modulations: BPSK, QPSK, 8/16/32/64/128/256-PSK, PAM4, 16/32/64/128/256-QAM, GFSK, CPFSK, B-FM, DSB-AM, SSB-AM and OQPSK.
 This is consistent with other experimental settings used in the field \cite{}.
-% Avoided highlighting that analog modulations are not used (not viable with our methodology, would have to be ignored)
-For all settings, we use 200KHz for the sampling frequency.
+We note that due to implementation difficulties, the last six modulations are ignored by maximum likelihood.
+Thus, the probability of this classes will be one when used, and zero when not.
+For all settings, we consider that the signal sampling frequency is 200KHz.
+We generate 234000 signals for training, and 26000 for testing.
+The duration of the signal is set to 1024 samples, for consistency with other similar datasets \cite{}.
+For the network, we use a ResNet-based network architecture \cite{}.
+We train the network for 100 epochs using SGD optimization with momentum 0.9 and learning rate 0.01, decaying exponentially at a rate of 0.95 per epoch.
+We use gradient clipping of size 5 and weight decay of 5e-4.
 
@@
 For the transmitter, we use 8 samples per symbol and a root raised cosine filter with rolloff 0.35.
+The results of using the different methodologies are shown in Table \ref{tab:sbasic}.
 
-For the second scenario, we additionally vary the transmitter settings. We consider either 2, 4, 8 or 16 samples per symbol and the rolloff of the filter can range from 0.15 to 0.45.
+For the second scenario, we additionally vary the transmitter settings.
+We consider either 2, 4, 8 or 16 samples per symbol and the rolloff of the filter can range from 0.15 to 0.45.
+The results of using the different methodologies are shown in Table \ref{tab:sawgn2p}.
 
 For the third and final scenario, we use the transmitter settings of the first scenario, but we consider also Rician and Rayleigh channels with AWGN noise.
+The results of using the different methodologies are shown in Table \ref{tab:sp0c20}.
 % Maybe specify the parameters used in both channels...
+
+\begin{table}[htbp]
+	\centering
+	%\small
+	\begin{tabular}{c|cc}
+	    Method & Accuracy & Robustness \\
+		\hline
+		ST & $85.87 \pm 0.02$ & $19.51 \pm 0.25$ \\ 
+		ST\_LNR & $86.34 \pm 0.52$ & $24.61 \pm 1.09$ \\ 
+		ST\_ML & $86.59 \pm 0.32$ & $27.30 \pm 0.47$ \\ 
+		AT & nan \\ 
+		AT\_LNR & nan \\ 
+		AT\_ML & nan \\ 
+    \end{tabular}
+    \caption{Accuracy and robustness for the ResNet model on the first dataset. The adversarial attacks are crafted using $l_{\infty}$ PGD-7 of 20 dB SPR.}
+    \label{tab:sbasic}
+\end{table}
+
+\begin{table}[htbp]
+	\centering
+	%\small
+	\begin{tabular}{c|cc}
+	    Method & Accuracy & Robustness \\
+		\hline
+		ST & $85.78 \pm 0.10$ & $20.56 \pm 1.14$ \\ 
+		ST\_LNR & $86.21 \pm 0.08$ & $22.82 \pm 0.88$ \\ 
+		ST\_ML & $\textbf{86.58} \pm 0.22$ & $\textbf{24.08} \pm 2.66$ \\
+        \hline
+		AT & $59.61 \pm 6.44$ & $55.45 \pm 3.64$ \\ 
+		AT\_LNR & $64.53 \pm 1.76$ & $\textbf{59.05} \pm 1.42$ \\ 
+		AT\_ML & $\textbf{65.06} \pm 1.77$ & $58.72 \pm 0.83$ \\ 
+    \end{tabular}
+    \caption{Accuracy and robustness for the ResNet model when varying the transmission settings on a gaussian channel.}
+    \label{tab:sawgn2p}
+\end{table}
+
+\begin{table}[htbp]
+	\centering
+	%\small
+	\begin{tabular}{c|cc}
+	    Method & Accuracy & Robustness \\
+		\hline
+		ST & $78.33 \pm 0.03$ & $18.83 \pm 2.59$ \\ 
+		ST\_LNR & $78.07 \pm 0.05$ & $17.86 \pm 3.31$ \\ 
+		ST\_ML & $78.27 \pm 0.06$ & $20.73 \pm 1.40$ \\ 
+		AT & nan \\ 
+		AT\_LNR & nan \\ 
+		AT\_ML & nan \\ 
+    \end{tabular}
+    \caption{Accuracy and robustness for the ResNet model on the third dataset. The adversarial attacks are crafted using $l_{\infty}$ PGD-7 of 20 dB SPR.}
+    \label{tab:sp0c20}
+\end{table}
 

### 2022-09-27 src/exec/local.sh

@@ -1,0 +1,10 @@
+for seed in 0
+do
+    for dataset in sp0c20
+    do
+        for loss in at_ml at_lnr at_aml
+        do
+            python src/main.py --dataset $dataset --loss $loss --n_epochs 100 --sch_gamma 0.95 --id $loss --batch_size 1024 --seed $seed --data_path /mnt/Data/Datasets
+        done
+    done
+done

### 2022-09-27 src/kdmc/data/synthetic.py

@@ -34,7 +34,7 @@ def split_synthetic_dataset(dataset, seed=0):
 
 
 class Synthetic(Dataset, ABC):
-    """Dataset class. They normally have 2.6M samples in total."""
+    """Dataset class. They normally have 260000 samples in total."""
 
     ALL_CLASSES = np.array([
         "BPSK", "QPSK", "8-PSK",

### 2022-10-01 src/kdmc/train/at.py
Fix bug in at_lnr

@@ -149,6 +149,7 @@ class LNRATTrainer(Trainer):
             ml_preds = ml_preds[lnr_mask]
 
             snr = batch['snr'].to(self.device)
+            snr = snr[lnr_mask]
             adv_inputs = self.atk(inputs, targets, snr)
             outputs = self.net(adv_inputs)
 

### 2022-10-03 src/exec/0.sh
Solve conflict

@@ -1,11 +1,10 @@
-python src/main.py --dataset sp0c20 --loss std --n_epochs 100 --sch_gamma 0.95 --id std --batch_size 1024 --dataset_size 1000000
-python src/main.py --dataset sp0c20 --loss std_ml --n_epochs 100 --sch_gamma 0.95 --id std_ml --batch_size 1024 --dataset_size 1000000
-python src/main.py --dataset sp0c20 --loss std_lnr --n_epochs 100 --sch_gamma 0.95 --id std_lnr --batch_size 1024 --dataset_size 1000000
-
-python src/main.py --dataset sbasic --loss std --n_epochs 100 --sch_gamma 0.95 --id std --batch_size 1024 --dataset_size 1000000
-python src/main.py --dataset sbasic --loss std_ml --n_epochs 100 --sch_gamma 0.95 --id std_ml --batch_size 1024 --dataset_size 1000000
-python src/main.py --dataset sbasic --loss std_lnr --n_epochs 100 --sch_gamma 0.95 --id std_lnr --batch_size 1024 --dataset_size 1000000
-
-python src/main.py --dataset sawgn2p --loss std --n_epochs 100 --sch_gamma 0.95 --id std --batch_size 1024 --dataset_size 1000000
-python src/main.py --dataset sawgn2p --loss std_ml --n_epochs 100 --sch_gamma 0.95 --id std_ml --batch_size 1024 --dataset_size 1000000
-python src/main.py --dataset sawgn2p --loss std_lnr --n_epochs 100 --sch_gamma 0.95 --id std_lnr --batch_size 1024 --dataset_size 1000000
+for seed in 0
+do
+    for dataset in sp0c20
+    do
+        for loss in at_lnr
+        do
+            python src/main.py --dataset $dataset --loss $loss --n_epochs 100 --sch_gamma 0.95 --id $loss --batch_size 1024 --seed $seed
+        done
+    done
+done

### 2022-10-03 src/exec/1.sh

@@ -2,7 +2,8 @@ for seed in 0
 do
     for dataset in sbasic
     do
-        for loss in std std_ml std_lnr
+        spr=20
+        for loss in at at_ml at_lnr
         do
             python src/main.py --dataset $dataset --loss $loss --n_epochs 100 --sch_gamma 0.95 --id $loss --batch_size 1024 --seed $seed
             for dataset_size in 100000 1000000

### 2022-10-03 src/exec/2.sh

@@ -1,8 +1,8 @@
-for seed in 1
+for seed in 3
 do
-    for dataset in sawgn2p
+    for dataset in sp0c20
     do
-        for loss in at at_ml at_lnr
+        for loss in at_lnr at_ml
         do
             python src/main.py --dataset $dataset --loss $loss --n_epochs 100 --sch_gamma 0.95 --id $loss --batch_size 1024 --seed $seed
         done

### 2022-10-03 paper/main.tex

@@
 
-\title{ML distillation
+\title{Improving modulation classification by distilling maximum likelihood
 \thanks{This work has been sponsored by armasuisse Science and Technology with the project ARNO (project code ???).}
@@
 \begin{abstract}
+In communication systems, there are many tasks, like modulation classification, for which Deep Neural Networks (DNNs) have obtained promising performance.
+However, these models have been shown to be susceptible to adversarial perturbations, namely imperceptible additive noise crafted to induce misclassification.
+This raises questions about the security but also about the general trust in model predictions.
+We propose to use adversarial training, which consists of fine-tuning the model with adversarial perturbations, to increase the robustness of automatic modulation classification (AMC) models.
+We show that current state-of-the-art models can effectively benefit from adversarial training, which mitigates the robustness issues for some families of modulations.
+We use adversarial perturbations to visualize the learned features, and we found that the signal symbols are shifted towards the nearest classes in constellation space, like maximum likelihood methods when adversarial training is enabled.
+This confirms that robust models are not only more secure, but also more interpretable, building their decisions on signal statistics that are actually relevant to modulation classification.
 \end{abstract}
@@
 
+% AMC, deep learning is being used. Different solutions
+Multiple civil and military applications in communication systems require recognizing with what modulation the information received was encoded.
+This leads to the use of Automatic Modulation Classification (AMC) on applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
+With the emergence of deep learning \cite{goodfellow2016deep}, neural networks made their way into AMC, and are currently the main and most effective method that tackles this problem \cite{OShea_Roy_Clancy_2018}.
+Compared with previous methods, like feature extraction \cite{xie2008efficient,zhou2013design,zhang2017wireless} or maximum likelihood functions \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, neural networks are relatively fast, adaptable to any channel characteristics, and their performance scales well with high quantities of data.
+
+% Effect of adversarial perturbations.
+% TODO: maybe add motivation of why robust models are important
 %
-
-Deep learning \cite{goodfellow2016deep}
-
-%Adversarial perturbations
-Recent studies have highlighted security issues in DNNs models \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}.
-Specifically, those models have been shown to be vulnerable to adversarial examples, which are carefully crafted but almost imperceptible perturbations, namely adversarial perturbations, that are added to a real data sample.
-For AMC, a perturbation can be crafted by solving the following optimization:
+Recent studies have highlighted that the neural networks used in AMC are susceptible to adversarial attacks \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}, in which carefully crafted but almost imperceptible perturbations are added to the transmitted signal.
+These adversarial perturbations can be used as an effective way of jamming wireless communication systems, requiring much less energy and being stealthier than normal attacks.
+To craft them, algorithms like FGSM \cite{Goodfellow_Shlens_Szegedy_2015} or PGD \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} are typically used to solve the following optimization:
 \begin{equation}
@@
 \end{equation}
+where $\delta_i^*$ is the adversarial perturbation added to the received signal $x_i$, $y_i$ is the one-hot-encoded vector of length K that encodes the modulation used, $\Ls$ is the cross-entropy loss, $f_{\theta}$ is the neural network defined with weights $\theta$, and $\varepsilon$ is a fixed value that constrains the norm of the perturbation to be small and imperceptible.
+
+% Defenses. Relationship with data. Knowledge distillation
+Some defenses have been proposed to make networks more robust, like adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019}, but it comes at a cost in accuracy and computational time.
+Some works have instead tried to understand why networks are susceptible, and label noise has been pointed as one of the main causes \cite{sanyal2020benign}.
+This is consistent with the increase in robustness when using knowledge distillation in combination with adversarial training~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits}, essentially training a student model with labels based on the teacher predictions.
+
+% Our work, what are the main motivations. Contributions.
+In this work, we propose a data-centric approach with the purpose of making neural networks more accurate and robust to adversarial attacks.
+Motivated by the success of knowledge distillation, we propose to reduce the label noise in the training data by using the theoretical class probabilities, derived from the noise distribution of the channel with the maximum likelihood function.
+We show that neural networks trained with these probabilities perform better than if trained with the original labels, confirming the effect of label noise in robustness.
+
+\section{Related Work}
+
+% Maximum likelihood. 
+%   (More details can be found in "Survey of automatic modulation classification techniques").
+Maximum likelihood \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution of the AMC task.
+It computes the likelihood function of the received signal with all possible modulations and estimates the most likely modulation.
+While in theory this is Bayes-optimal, it is computationally expensive and requires prior knowledge of the channel characteristics, so sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009}.
+
+% Recent approaches. Explain and reference.
+Deep learning \cite{goodfellow2016deep} has been proposed as a better solution to recognize modulations.
+%In comparison with the above approaches, it has two clear advantages.
+It has low complexity which, unlike maximum likelihood methods, scales linearly, and can be trained end-to-end.
+This increases the quantity and quality of features extracted from the data compared to feature recognition methods.
+It also allows for extra flexibility, since it does not require any assumption on the channel conditions but learns them directly from the data.
+There are mainly two types of Deep Learning models for modulation recognition.
+On the one hand, inspired by success in speech recognition, some works \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} propose architectures based on long short-term memory networks (LSTMs) \cite{Hochreiter_Schmidhuber_1997} for modulation recognition.
+On the other hand, other works \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019} employ convolutional neural networks (CNNs) \cite{Krizhevsky_Sutskever_Hinton_2017}, which have been successful in computer vision thanks to their ability to induce translation invariance on the input.
+The current state-of-the-art in modulation recognition \cite{OShea_Roy_Clancy_2018} uses a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}.
+However, despite their improved performance, there are drawbacks in deep learning approaches compared with the classical methods.
+In particular, they are black-box models, making them much less interpretable than their classical counterparts, and they are vulnerable to crafted small energy perturbations, which compromise the security of the system against malicious attacks.
+
+% Defenses to adversarial attacks
+Adversarial perturbations have also been shown to fool DNNs trained for the task of modulation recognition in a recent work \cite{Sadeghi_Larsson_2019}.
+The authors propose to make the power of the perturbation dependent on the signal power.
+They fix the ratio between the signal and the perturbation power, or signal-to-perturbation ratio (SPR), when studying the effect of the perturbations.
+They test two different scenarios: white-box attacks, where the attacker has access to the model gradients, and black-box attacks, where only the prediction can be accessed.
+For the white-box setting, they use the Fast Gradient Sign Method (FGSM) \cite{Goodfellow_Shlens_Szegedy_2015} to craft the perturbations, and found that adversarial perturbations require much less power than additive white gaussian noise (AWGN) to fool the network.
+The authors in \cite{Flowers_Buehrer_Headley_2019} further expand over prior work \cite{Sadeghi_Larsson_2019} using the bit error rate (BER) as a measure of distortion.
+Additionally, they consider the scenario where the adversarial perturbation is crafted at the transmitter in order to protect the model against eavesdropping.
+However, in the work they assume perfect knowledge of the DNN used by the eavesdropper, which we think is unrealistic and would fail if there are several eavesdroppers using different modulation recognition models.
+
+% Knowledge distillation
+KD consists on training a student model to mimic the outputs of a teacher model.
+To that end, most KD methods~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} append a matching function to the loss which encourages the final representations of the teacher and the student to be close at every sample.
+While these methods are effective in transferring clean performance, they are not able to transfer robustness against adversarial examples~\cite{goldblum2020adversarially}.
+For this reason, recent works have proposed alternatives to address this problem~\cite{goldblum2020adversarially,zi2021revisiting,zhu2021reliable,shao2021and,maroto2022benefits}, that encourage robustness by matching the output of the teacher and student models in the adversarial examples as well.
 
@@
 Thus, the network will be optimized to be as confident and accurate as possible on the training set.
-However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals this may no longer the case.
-The reason is that there could be a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict.
-In some extreme cases, the noise can even make the task impossible to solve, where the signal received could have been generated from any of multiple modulations with similar probability.
+However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals typically there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict.
+Such cases are numerous when testing models in the AMC literature, where the signal received could have been generated from any of multiple modulations with similar probability.
 
-In many other tasks, these probabilities would be difficult or impossible to obtain.
-However, in AMC, there is an optimal method that gives us these probabilities with perfect accuracy: Maximum Likelihood (ML).
-Despite its optimal performance, neural networks are still preferred over ML for a simple reason: ML does not perform well when we do not have full knowledge of the channel effects on the signal.
-In fact, even if we were to estimate the channel, any small deviation from the real channel parameters has a major effect on the ML performance.
-Moreover, incorporating this uncertainty in the ML formulation makes it computationally unfeasible.
+While in many other tasks, these probabilities would be difficult or impossible to obtain, in AMC, we can use the maximum likelihood (ML) function to derive the real probabilities.
+Due to the characteristics of ML, this is only computationally feasible on coherent scenarios, where we have prior knowledge of the channel conditions.
+Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and given the received symbols $r(x)$, where $r$ applies the proper communication filter and downsampling to the received signal, the corresponding ML function is described as
+\begin{equation}
+	f_{i}(r(x)) = \dfrac{1}{2\pi \sigma^{2}|M_i|}\prod_{t=1}^{T} \sum_{j=1}^{|M_i|} \exp\left(-\dfrac{\lVert r(x)_t - s_j\rVert^{2}}{2 \sigma^{2}}\right)
+\end{equation}
+where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that correspond to the state $j$.
+Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$
+
+The reason why ML is not prefered over neural networks is simple: they perform badly on non-coherent scenarios, where the channel or transmision filter parameters are unknown.
+Moreover, any small deviation from the real channel parameters has a major effect on the ML performance, which discards the possibility of trying to estimate these parameters.
+Moreover, incorporating the parameter uncertainty in the ML formulation makes it much more costly computationally without being more performant than neural networks.
 
@@
 		ST\_ML & $86.59 \pm 0.32$ & $27.30 \pm 0.47$ \\ 
-		AT & nan \\ 
-		AT\_LNR & nan \\ 
-		AT\_ML & nan \\ 
+		AT & $57.36 \pm 3.12$ & $54.71 \pm 2.67$ \\ 
+		AT\_LNR & $64.50 \pm 0.62$ & $58.44 \pm 0.60$ \\ 
+		AT\_ML & $67.01 \pm 1.04$ & $59.44 \pm 0.32$ \\ 
     \end{tabular}
@@
 		\hline
-		ST & $78.33 \pm 0.03$ & $18.83 \pm 2.59$ \\ 
-		ST\_LNR & $78.07 \pm 0.05$ & $17.86 \pm 3.31$ \\ 
-		ST\_ML & $78.27 \pm 0.06$ & $20.73 \pm 1.40$ \\ 
-		AT & nan \\ 
-		AT\_LNR & nan \\ 
-		AT\_ML & nan \\ 
+		ST & $78.34 \pm 0.02$ & $18.86 \pm 1.83$ \\ 
+		ST\_LNR & $78.08 \pm 0.04$ & $18.97 \pm 3.03$ \\ 
+		ST\_ML & $78.40 \pm 0.22$ & $20.00 \pm 1.61$ \\ 
+		AT & $49.00 \pm nan$ & $45.36 \pm nan$ \\ 
+		AT\_LNR & $48.16 \pm nan$ & $46.02 \pm nan$ \\ 
+		AT\_NML & $39.78 \pm 0.14$ & $36.14 \pm 1.78$ \\ 
+		AT\_AML & $53.83 \pm 0.47$ & $47.04 \pm 0.07$ \\ 
     \end{tabular}
@@
 
+\section{Conclusion}
+
+% Future work: ML for Rayleigh/Rician channels. Use in other fields like physics. Test with other KD functions. More models.
+
 \bibliographystyle{IEEEbib}

### 2022-10-10 paper/main.tex
Final changes to 1st draft

--- 2022-09-24 paper/main.tex
@@
 \usepackage{hyperref}
+\usepackage{tikz}
+\usetikzlibrary{positioning}
 
@@
 
-\title{ML distillation
-\thanks{This work has been sponsored by armasuisse Science and Technology with the project ARNO (project code ???).}
+\title{Improving modulation classification by distilling maximum likelihood
+\thanks{This work has been sponsored by armasuisse Science and Technology under the project ARNO (project code ARAMIS 047-22).}
 }
@@
 \begin{abstract}
+Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) specifically, despite their susceptibility to adversarial perturbations, small carefully crafted noise that completely changes the network prediction.
+Recently, several works have shown the importance of robust models for security and interpretability, and methods like knowledge distillation and adversarial training have been proposed.
+In this work, we highlight the importance of the quality of the training data used by the model in its final robustness.
+We propose to use the Maximum Likelihood function to generate better training labels, that better teach the model to be uncertain under heavy channel corruptions.
+We show that this hybrid approach overcomes the limitations of Maximum Likelihood (e.g.
+requiring many priors) and it is quite effective at improving the robustness and the accuracy of neural networks.
 \end{abstract}
@@
 \begin{IEEEkeywords}
+Neural networks, robustness, Maximum Likelihood, knowledge distillation, automatic modulation classification
 \end{IEEEkeywords}
@@
 
+% AMC, deep learning is being used. Different solutions
+Multiple civil and military applications in communication systems require recognizing with what modulation the information received was encoded.
+This leads to the use of Automatic Modulation Classification (AMC) in applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
+With the emergence of deep learning \cite{goodfellow2016deep}, neural networks made their way into AMC, and are currently the main and most effective method that tackles this problem \cite{OShea_Roy_Clancy_2018}.
+Compared with previous methods, like feature extraction \cite{xie2008efficient,zhou2013design,zhang2017wireless} or maximum likelihood functions \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, neural networks are relatively fast, adaptable to any channel characteristics, and their performance scales well with high quantities of data.
+
+% Effect of adversarial perturbations.
+% TODO: maybe add motivation of why robust models are important
 %
+Recent studies have highlighted that the neural networks used in AMC are susceptible to adversarial attacks \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}, in which carefully crafted but almost imperceptible perturbations are added to the transmitted signal.
+These adversarial perturbations can be used as an effective way of jamming wireless communication systems, requiring much less energy and being stealthier than normal attacks.
+To craft them, algorithms like FGSM \cite{Goodfellow_Shlens_Szegedy_2015} or PGD \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} are typically used to solve the following optimization:
+\begin{equation}
+\label{eq:adv_pert}
+    \delta_i^* = \argmax_{\delta_i}\Ls(f_{\theta}(x_i + \delta_i), y_i) \quad \text{s.t.} \quad \lVert \delta_i \rVert_{\infty} \leq \varepsilon
+\end{equation}
+where $\delta_i^*$ is the adversarial perturbation added to the received signal $x_i$, $y_i$ is the one-hot-encoded vector of length K that encodes the modulation used, $\Ls$ is the cross-entropy loss, $f_{\theta}$ is the neural network defined with weights $\theta$, and $\varepsilon$ is a fixed value that constrains the norm of the perturbation to be small and imperceptible.
 
-Deep learning \cite{goodfellow2016deep}
+% Defenses. Relationship with data. Knowledge distillation
+Some defenses have been proposed to make networks more robust, like adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019}, but it comes at a cost in accuracy and computational time.
+Some works have instead tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
+This is consistent with the increase in robustness when using knowledge distillation in combination with adversarial training~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits}, essentially training a student model with labels based on the teacher predictions.
+
+% Our work, what are the main motivations. Contributions.
+In this work, we propose a data-centric approach with the purpose of making neural networks more accurate and robust to adversarial attacks.
+Motivated by the success of knowledge distillation, we propose to reduce the label noise in the training data by using the theoretical class probabilities, derived from the noise distribution of the channel with the maximum likelihood function.
+We show that neural networks trained with these probabilities perform better than if trained with the original labels, confirming the effect of label noise in robustness.
+
+\section{Related Work}
+
+% Maximum likelihood. 
+%   (More details can be found in "Survey of automatic modulation classification techniques").
+Maximum likelihood \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution for the AMC task.
+It computes the likelihood function of the received signal with all possible modulations and estimates the most likely modulation.
+Despite being Bayes-optimal, because it can be computationally expensive and requires prior knowledge of the channel characteristics, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009}.
+
+% Recent approaches. Explain and reference.
+Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC that avoids these shortcomings.
+Inspired by success in speech recognition, some works \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} propose architectures based on long short-term memory networks (LSTMs) \cite{Hochreiter_Schmidhuber_1997}.
+Other works \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019} employ convolutional neural networks (CNNs) \cite{Krizhevsky_Sutskever_Hinton_2017} instead, which have been highly successful in computer vision tasks.
+Particularly, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures.
+Other works use neural architecture search (NAS) \cite{ahmadi2008modulation,dai2019multi,perenda2021evolutionary} to trade off performance with computational speed.
+However, all neural networks have common drawbacks: they are black-box models, less interpretable than their classical counterparts, and they are susceptible to adversarial perturbations, compromising the security of the system against malicious attacks.
+
+% Defenses to adversarial attacks
+Adversarial perturbations have been shown to fool neural networks in AMC \cite{Sadeghi_Larsson_2019,maroto2021benefits}.
+Unlike in other fields, in AMC the power of the perturbation is made dependent on the signal power with the signal-to-perturbation ratio (SPR).
+Some defenses have been proposed to make models more robust against adversarial perturbations.
+Adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} has been shown to be effective in AMC \cite{maroto2021safeamc,manoj2022toward}.
+Randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have also been successful in making neural networks more robust.
+
+% Knowledge distillation
+Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance.
+However, these approaches do not help the student network in benefitting from the higher adversarial robustness that a teacher network could have~\cite{goldblum2020adversarially}.
+However, recently, there are works that have proposed alternative loss functions that address this problem~\cite{goldblum2020adversarially,zi2021revisiting,zhu2021reliable,shao2021and,maroto2022benefits}.
+These solutions encourage and improve the student robustness by matching its output with the teacher outputs on adversarial examples as well as clean examples.
 
@@
 
-Normally, to perform well on automatic modulation classification (AMC), neural networks are trained to infer the modulation used in transmission from the signal received.
+Normally, to perform well on AMC, neural networks are trained to infer the modulation used in transmission from the signal received.
 Thus, the network will be optimized to be as confident and accurate as possible on the training set.
-However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals this may no longer the case.
-The reason is that there could be a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict.
-In some extreme cases, the noise can even make the task impossible to solve, where the signal received could have been generated from any of multiple modulations with similar probability.
+However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals typically there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict.
+Such cases are numerous when testing models in the AMC literature, where the signal received could have been generated from any of multiple modulations with similar probability.
 
-In many other tasks, these probabilities would be difficult or impossible to obtain.
-However, in AMC, there is an optimal method that gives us these probabilities with perfect accuracy: Maximum Likelihood (ML).
-Despite its optimal performance, neural networks are still preferred over ML for a simple reason: ML does not perform well when we do not have full knowledge of the channel effects on the signal.
-In fact, even if we were to estimate the channel, any small deviation from the real channel parameters has a major effect on the ML performance.
-Moreover, incorporating this uncertainty in the ML formulation makes it computationally unfeasible.
+While in many other tasks, these probabilities would be difficult or impossible to obtain, in AMC, we can use the maximum likelihood (ML) function to derive the real probabilities.
+Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
+Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and given the received symbols $r(x)$, where $r$ applies the proper communication filter and downsampling to the received signal.
+We show in Figure \ref{fig:comm_system} a diagram describing the communication system.
+We highlight that while the neural network has to process directly what the receptor receives, maximum likelihood processes the symbols of that signal instead.
+This is possible because we can assume we know the communication filter and upsampling used in the transmitter, which we can invert at the receptor.
+The ML function when the channel is gaussian is given by the following expression
+\begin{equation}
+	f_{i}(r(x)) = \dfrac{1}{2\pi \sigma^{2}|M_i|}\prod_{t=1}^{T} \sum_{j=1}^{|M_i|} \exp\left(-\dfrac{\lVert r(x)_t - s_j\rVert^{2}}{2 \sigma^{2}}\right)
+\label{eq:ml}
+\end{equation}
+where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that correspond to the state $j$.
+Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$.
+
+\begin{figure}
+\begin{tikzpicture}[
+	greennode/.style={rectangle, draw=green!60, fill=green!5, very thick, minimum size=5mm},
+	graynode/.style={rectangle, draw=gray!60, fill=gray!5, very thick, minimum size=5mm},
+	]
+	%Nodes
+	\node[graynode,text width=1.5cm,text centered](mod){Modulator\\(y)};
+	\node[graynode](tf)[minimum height = 1cm][text centered][right=0.25cm of mod]{$r'(x)$};
+	\node[graynode](channel)[minimum height = 1cm, right=0.25cm of tf]{Channel};
+	\node[graynode](rf)[minimum height = 1cm, right=0.25cm of channel]{$r(x)$};
+	\node[graynode](dem)[minimum height = 1cm, text width=1.85cm][text centered][right=0.25cm of rf]{Demodulator\\(pred)};
+
+	\node[greennode](nn)[minimum height = 1cm, text width=1.25cm][text centered][below=0.25cm of channel]{Neural\\Network};
+	\node[greennode](ml)[minimum height = 1cm][text centered][below=0.25cm of rf]{ML};
+
+	%Lines
+	\draw[->] (mod.east) -- (tf.west);
+	\draw[->] (tf.east) -- (channel.west);
+	\draw[->] (channel.east) -- (rf.west);
+	\draw[->] (rf.east) -- (dem.west);
+	\draw[->] (channel.south) -- (nn.north);
+	\draw[->] (rf.south) -- (ml.north);
+
+\end{tikzpicture}
+\caption{Simplified diagram of the communication system.
+The transmitter sends the binary data using the modulator, which converts the data into symbols, and $r'(x)$, which upsamples the signal and passes it through a communication filter (e.g.
+root raised cosine).
+The signal passes through the communication channel, which adds noise and distortion to the signal.
+The receptor does the inverse operation and demodulates the signal based on the neural network prediction.
+As shown, the signals used by the neural network and ML are slightly different.}
+\label{fig:comm_system}
+\end{figure}
+
+The reason why ML is not preferred over neural networks is simple: they perform badly in non-coherent scenarios, where the channel or transmission filter parameters are unknown.
+Moreover, any small deviation from the real channel parameters has a major effect on the ML performance, which discards the possibility of trying to estimate these parameters.
+Moreover, incorporating the parameter uncertainty in the ML formulation makes it much more costly computationally without being more performant than neural networks.
 
@@
 We will use a neural network for inference, but we will train it with the probabilities given by maximum likelihood.
+Because Equation \ref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities.
 This is feasible when we consider that we can have full knowledge of the channel conditions by generating the training samples ourselves.
@@
 
-\section{Knowledge distillation}
+\section{Maximum likelihood distillation}
+
+Typically in AMC, neural networks try to fit a function that takes as input the received signal data and outputs the modulation used by the transmitter.
+Thus, the corresponding loss that the model uses to train is given by the standard training loss
+\begin{equation}
+    \text{ST} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), y_i)
+\end{equation}
+where $N$ is the size of the training set.
+
+However, in practice, the neural network is trained with noisy signals where the modulation that was used cannot be inferred so easily.
+Intuitively, for these signals we would like the outputs of the network to rely on this sense of uncertainty.
+Thus, with similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in the corresponding coherent scenario.
+\begin{equation}
+    \text{ST\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), p_{ML}(r(x_i)))
+\label{eq:st_ml}
+\end{equation}
+where $p_{ML}$ is the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal.
+Because $r$ and $p_{ML}$ are functions that depend on information that is not known in non-coherent scenarios, we propose to use this loss function only when training the network, where this information can be known.
+
+The main downside of using this function is that, while the probabilities given by ML are optimal in the context of a coherent scenario, they differ from the real probabilities $p^{*}$ that are conditional to the channel and communication filter distributions, $H$.
+However, our hypothesis, which we test in the following Section, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which enforce full confidence on all samples, no matter how noisy they are.
+Mathematically, these probabilities are related by the following expression:
+\begin{equation}
+	p[m|x] =  \sum_i p[m|x,H=h_i] \cdot p[H=h_i|x]
+\end{equation}
+where $m$ is the vector of all modulations, $h_i$ is one of the possible coherent scenarios where the true coherent scenario is assigned to $h_0$ without loss of generality.
+Thus, $p[m|x] = p^{*}$ and $p_{ML} = p[m|x,H=h_0]$.
+Based on this formulation, our model will match better $p^{*}$ when the true communication parameters $H=h_0$ can be easily predicted from x ($p[H=h_0|x] \approx 1$) or when the communication parameters do not affect that much the probabilities ($p[m|x,H=h_i] \approx p_{ML} \; \forall i$).
+
+Additionally, we propose a middle-ground approach, where instead of training the model on the ML probabilities, we use these probabilities to determine if the true label is incorrect.
+This happens in very noisy scenarios, where the noise added to the signal may change the true class of the signal by pure chance.
+Intuitively, training on these signals will potentially confuse the network.
+Thus, we will use standard training loss but removing the label noise by training only on the signals where this does not happen:
+\begin{equation}
+    \text{ST\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i), y_i)
+\end{equation}
+where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i)))$.
+
+While the previous proposals are effective in incorporating the ML information to train the model, they do not address directly the vulnerability of neural networks to adversarial perturbations.
+One of the most straightforward ways to improve the network robustness is to use the adversarial training loss function
+\begin{equation}
+    \text{AT} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), y_i)
+\end{equation}
+where $x_i' = x_i + \delta_i^*$ is a crafted adversarial signal that maximizes the cross-entropy loss of the neural network in the neighborhood of $x_i$.
+
+Analogously to Equation \ref{eq:st_ml}, we propose the following loss to match the model to the ML probabilities
+\begin{equation}
+    \text{AT\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(x_i')))
+\end{equation}
+We highlight that, unlike the analogous standard training function, we have to make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.
+This assumption holds when the adversarial perturbation is sufficiently small, which is normally the case during adversarial training.
+
+One way to reduce the effect of this assumption is to instead remove label noise using ML
+\begin{equation}
+    \text{AT\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i'), y_i)
+\end{equation}
+where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i')))$.
+Even if $p_{ML}$ is not strictly correct due to the adversarial perturbation being relatively large, it will tend to remove signals that are already very noisy, thus greatly reducing the chance of label noise affecting adversarial training.
+Since label noise has a direct impact on the robustness of the network, we expect label noise removal to be particularly effective.
+
+For training with non-gaussian channels, because we remove the Rayleigh/Rician components, we have the drawback that we cannot directly translate the adversarial perturbation added to the neural network to the signal received by ML.
+For that reason, we have considered the following two solutions: to use the ML probabilities of the uncorrupted signal as follows
+\begin{equation}
+    \text{AT\_NML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(g_i))
+\label{eq:at_nml}
+\end{equation}
+and to recompute the adversarial perturbation but for the ML function using the following loss function
+\begin{equation}
+    \text{AT\_AML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(g_i)'))
+	\label{eq:at_aml}
+\end{equation}
+where $g_i$ is the received signal when the Rayleigh/Rician effects are removed and $r(g_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of ML in the neighborhood of $r(g_i)$.
+
+We will show that adversarial perturbations change greatly the probabilities of the received signal, making it desirable to use AT\_AML over AT\_NML.
 
@@
 We propose to evaluate our methodology on scenarios with different levels of non-coherence.
-This way, we can verify if the probabilities generated by maximum likelihood in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions.
-For all the experiments the task will be the same.
-We will train the neural network to be able to distinguish between the following digital modulations: BPSK, QPSK, 8/16/32/64/128/256-PSK, PAM4, 16/32/64/128/256-QAM.
-This is consistent with other experimental settings used in the field \cite{}.
-% Avoided highlighting that analog modulations are not used (not viable with our methodology, would have to be ignored)
-For all settings, we use 200KHz for the sampling frequency.
+This way, we can verify if the probabilities generated by ML in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions.
+
+For all the experiments, we train the neural network to distinguish between the following digital modulations: BPSK, QPSK, 8/16/32/64/128/256-PSK, PAM4, 16/32/64/128/256-QAM, GFSK, CPFSK, B-FM, DSB-AM, SSB-AM, and OQPSK \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020}.
+For the last six modulations, the ML formulation cannot be directly applied, so we use the original labels $y$ on these cases.
+For all settings, we consider that the signal sampling frequency is 200KHz.
+We generate 234000 signals for training and 26000 for testing.
+The duration of the signal is set to 1024 samples, for consistency with other similar datasets \cite{OShea_West_2016}.
+For the network, we use a ResNet-based network architecture \cite{OShea_Roy_Clancy_2018}, that while being fast to train has great performance in AMC.
+We train the network for 100 epochs using SGD optimization with momentum 0.9 and learning rate 0.01, decaying exponentially at a rate of 0.95 per epoch.
+We use gradient clipping of size 5 and weight decay of 5e-4.
+When computing the adversarial perturbations for both training and testing the robustness of the network, we use PGD-7 with $\varepsilon=20 \text{dB SPR}$ (signal-to-perturbation ratio).
 
@@
 For the transmitter, we use 8 samples per symbol and a root raised cosine filter with rolloff 0.35.
+Table \ref{tab:sbasic} proves that the network is much more effective when we remove the label noise, both in the standard and adversarial training scenarios.
+The increase in robustness is much more significant, which confirms our expectations.
+However, when using the ML probabilities, we get the biggest increase in performance, which underlines the benefit of distinguishing between uncertain and certain predictions.
 
-For the second scenario, we additionally vary the transmitter settings. We consider either 2, 4, 8 or 16 samples per symbol and the rolloff of the filter can range from 0.15 to 0.45.
+For the second scenario, we additionally vary the transmitter settings.
+We consider either 2, 4, 8, or 16 samples per symbol and the rolloff of the filter can range from 0.15 to 0.45.
+Table \ref{tab:sawgn2p} shows very similar results as the previous case.
+However, since there are more parameter configurations, the difference between $p_{ML}$ and $p^{*}$ increases, which shows in the lower increase in performance between LNR and ML methodologies overall.
 
 For the third and final scenario, we use the transmitter settings of the first scenario, but we consider also Rician and Rayleigh channels with AWGN noise.
-% Maybe specify the parameters used in both channels...
+Table \ref{tab:sp0c20} shows smaller improvements compared to the two previous cases.
+While the probabilities of ML are not discerning well the label noise, which shows in the lack of improvement for the LNR methods, they can still help the network as seen in the ML methods.
+We highlight that for adversarial training is much more preferable to perturb the signal received by ML before computing the probabilities, due to these probabilities being much more representative of the signal used by the model than the probabilities in the unperturbed point.
+
+\begin{table}[htbp]
+	\centering
+	%\small
+	\begin{tabular}{c|cc}
+	    Method & Accuracy & Robustness \\
+		\hline
+		ST & $85.87 \pm 0.02$ & $19.51 \pm 0.25$ \\ 
+		ST\_LNR & $86.34 \pm 0.52$ & $24.61 \pm 1.09$ \\ 
+		ST\_ML & $\textbf{86.59} \pm 0.32$ & $\textbf{27.30} \pm 0.47$ \\ 
+		\hline
+		AT & $57.36 \pm 3.12$ & $54.71 \pm 2.67$ \\ 
+		AT\_LNR & $64.50 \pm 0.62$ & $58.44 \pm 0.60$ \\ 
+		AT\_ML & $\textbf{67.01} \pm 1.04$ & $\textbf{59.44} \pm 0.32$ \\ 
+    \end{tabular}
+    \caption{Accuracy and robustness for the ResNet model when only varying the noise settings on a gaussian channel.}
+    \label{tab:sbasic}
+\end{table}
+
+\begin{table}[htbp]
+	\centering
+	%\small
+	\begin{tabular}{c|cc}
+	    Method & Accuracy & Robustness \\
+		\hline
+		ST & $85.78 \pm 0.10$ & $20.56 \pm 1.14$ \\ 
+		ST\_LNR & $86.21 \pm 0.08$ & $22.82 \pm 0.88$ \\ 
+		ST\_ML & $\textbf{86.58} \pm 0.22$ & $\textbf{24.08} \pm 2.66$ \\
+        \hline
+		AT & $59.61 \pm 6.44$ & $55.45 \pm 3.64$ \\ 
+		AT\_LNR & $64.53 \pm 1.76$ & $\textbf{59.05} \pm 1.42$ \\ 
+		AT\_ML & $\textbf{65.06} \pm 1.77$ & $58.72 \pm 0.83$ \\ 
+    \end{tabular}
+    \caption{Accuracy and robustness for the ResNet model when varying the noise level, the samples per symbol, and the transmitter communication filter on a gaussian channel.}
+    \label{tab:sawgn2p}
+\end{table}
+
+\begin{table}[htbp]
+	\centering
+	%\small
+	\begin{tabular}{c|cc}
+	    Method & Accuracy & Robustness \\
+		\hline
+		ST & $78.34 \pm 0.02$ & $18.86 \pm 1.83$ \\ 
+		ST\_LNR & $78.08 \pm 0.04$ & $18.97 \pm 3.03$ \\ 
+		ST\_ML & $\textbf{78.40} \pm 0.22$ & $\textbf{20.00} \pm 1.61$ \\
+		\hline
+		AT & $50.74 \pm 2.46$ & $\textbf{47.15} \pm 2.53$ \\ 
+		AT\_LNR & $48.49 \pm 0.46$ & $45.62 \pm 0.57$ \\  
+		AT\_NML & $42.11 \pm 4.66$ & $38.47 \pm 4.88$ \\  
+		AT\_AML & $\textbf{54.10} \pm 0.57$ & $\textbf{46.94} \pm 0.17$ \\ 
+    \end{tabular}
+    \caption{Accuracy and robustness for the ResNet model when varying the channel properties and the level noise.}
+    \label{tab:sp0c20}
+\end{table}
+
+\section{Conclusion}
+
+% Future work: ML for Rayleigh/Rician channels. Use in other fields like physics. Test with other KD functions. More models.
+We highlight in this work the benefits of incorporating theoretical models like maximum likelihood when training neural networks.
+We believe this is a crucial step to create networks that are more robust, which ensures higher trust in critical scenarios.
+We showed that networks are more robust when distilling the probabilities given by these mathematical models, even when they operate under different priors.
+
+For future work, we think this methodology can be explored in other fields like physics, where neural networks are being increasingly preferred over mathematical models.
+Even in AMC, it could be interesting to explore other knowledge distillation losses and to use better ML functions that are adapted to Rayleigh or Rician channels, to improve the results when considering multiple types of channels.
 

### 2022-10-13 paper/main.tex
Add mar feedback

@@
 \begin{abstract}
-Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) specifically, despite their susceptibility to adversarial perturbations, small carefully crafted noise that completely changes the network prediction.
+Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) specifically, despite their susceptibility to adversarial perturbations, i.e.
+small carefully crafted noise that completely changes the network prediction.
 Recently, several works have shown the importance of robust models for security and interpretability, and methods like knowledge distillation and adversarial training have been proposed.
@@
 We propose to use the Maximum Likelihood function to generate better training labels, that better teach the model to be uncertain under heavy channel corruptions.
-We show that this hybrid approach overcomes the limitations of Maximum Likelihood (e.g.
-requiring many priors) and it is quite effective at improving the robustness and the accuracy of neural networks.
+We show that this hybrid approach overcomes the limitations of Maximum Likelihood, like requiring the communication channel parameters as a prior, and it is quite effective at improving the robustness and the accuracy of neural networks.
 \end{abstract}
@@
 %   (More details can be found in "Survey of automatic modulation classification techniques").
-Maximum likelihood \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution for the AMC task.
+Maximum likelihood (ML) \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution for the AMC task.
 It computes the likelihood function of the received signal with all possible modulations and estimates the most likely modulation.
-Despite being Bayes-optimal, because it can be computationally expensive and requires prior knowledge of the channel characteristics, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009}.
+This method is Bayes-optimal, which means that it is the most accurate and adversarially robust model for AMC.
+However, it can be computationally expensive and requires prior knowledge of the channel characteristics, so sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009}.
 
@@
 % Knowledge distillation
-Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance.
+Knowledge distillation consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling}.
 However, these approaches do not help the student network in benefitting from the higher adversarial robustness that a teacher network could have~\cite{goldblum2020adversarially}.
@@
 
-While in many other tasks, these probabilities would be difficult or impossible to obtain, in AMC, we can use the maximum likelihood (ML) function to derive the real probabilities.
+While in many other tasks, these probabilities would be difficult or impossible to obtain, in AMC, we can use the ML function to derive the real probabilities.
 Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
@@
 The signal passes through the communication channel, which adds noise and distortion to the signal.
-The receptor does the inverse operation and demodulates the signal based on the neural network prediction.
+The receptor uses a coupled communication filter with downsampling, $r(x)$, and demodulates the signal based on the neural network prediction.
 As shown, the signals used by the neural network and ML are slightly different.}
@@
 where $p_{ML}$ is the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal.
-Because $r$ and $p_{ML}$ are functions that depend on information that is not known in non-coherent scenarios, we propose to use this loss function only when training the network, where this information can be known.
+We propose to use this loss function only during training, since $r$ and $p_{ML}$ are functions that require information that is unavailable in non-coherent scenarios (i.e.
+during test).
 
@@
 		AT & $59.61 \pm 6.44$ & $55.45 \pm 3.64$ \\ 
-		AT\_LNR & $64.53 \pm 1.76$ & $\textbf{59.05} \pm 1.42$ \\ 
-		AT\_ML & $\textbf{65.06} \pm 1.77$ & $58.72 \pm 0.83$ \\ 
+		AT\_LNR & $65.03 \pm 1.23$ & $59.20 \pm 1.34$ \\ 
+		AT\_ML & $\textbf{66.27} \pm 1.72$ & $\textbf{59.74} \pm 1.29$ \\ 
     \end{tabular}
@@
 		AT\_LNR & $48.49 \pm 0.46$ & $45.62 \pm 0.57$ \\ 
-		AT\_NML & $42.11 \pm 4.66$ & $38.47 \pm 4.88$ \\  
+		AT\_ML & $49.01 \pm 0.13$ & $45.07 \pm 0.56$ \\  
 		AT\_AML & $\textbf{54.10} \pm 0.57$ & $\textbf{46.94} \pm 0.17$ \\ 

### 2022-10-13 paper/main.tex
Add Pascal changes

--- 2022-10-10 paper/main.tex
@@
 
+\newcommand{\pf}[1]{{\textcolor{orange}{PF: {#1}}}}
+%\newcommand{\pf}[1]{} %cuncomment this one, and comment the previous line to remove all comments...
+
 % Latex math commands
@@
 
-\title{Improving modulation classification by distilling maximum likelihood
+\title{Improving modulation classification by distilling maximum likelihood \pf{Maximum Likelihood Distillation for Robust Modulation Classification}
 \thanks{This work has been sponsored by armasuisse Science and Technology under the project ARNO (project code ARAMIS 047-22).}
@@
 \begin{abstract}
-Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) specifically, despite their susceptibility to adversarial perturbations, small carefully crafted noise that completely changes the network prediction.
-Recently, several works have shown the importance of robust models for security and interpretability, and methods like knowledge distillation and adversarial training have been proposed.
-In this work, we highlight the importance of the quality of the training data used by the model in its final robustness.
-We propose to use the Maximum Likelihood function to generate better training labels, that better teach the model to be uncertain under heavy channel corruptions.
-We show that this hybrid approach overcomes the limitations of Maximum Likelihood (e.g.
-requiring many priors) and it is quite effective at improving the robustness and the accuracy of neural networks.
+Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) in particular.
+However, they are very susceptible to small adversarial perturbations that are carefully crafted to change the network decision.
+In this work, we build on knowledge distillation ideas and adversarial training in order to build more robust AMC systems.
+We first outline the importance of the quality of the training data in terms of accuracy and robustness of the model.
+We then propose to use the Maximum Likelihood function, which could solve the AMC problem in offline settings, to generate better training labels.
+Those teach the model to be uncertain in challenging conditions, which permits to increase the standard accuracy, as well as the robustness of the model when combined with adversarial training.
+\pf{add some quantitative notes or more precise information about the actual results.}\pf{recall contributions/benefits or add general perspectives about the potential of the proposal: so what?
+why is that a cool idea, a cool paper?} \pf{re-check the full paragraph}
 \end{abstract}
@@
 % AMC, deep learning is being used. Different solutions
-Multiple civil and military applications in communication systems require recognizing with what modulation the information received was encoded.
-This leads to the use of Automatic Modulation Classification (AMC) in applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
-With the emergence of deep learning \cite{goodfellow2016deep}, neural networks made their way into AMC, and are currently the main and most effective method that tackles this problem \cite{OShea_Roy_Clancy_2018}.
+Communication systems often require the receiver to recognize the modulation scheme that has been used to encode the transmitted signals.
+This is often refered as Automatic Modulation Classification (AMC) in applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
+The AMC task can be formaulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations.
+Even if the solution is Bayes-optimal, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009} because ML requires prior knowledge of the channel characteristics and is computationally complex to solve in realtime.
+
+Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC as neural networks are relatively fast at inference time, adaptable to any channel characteristics, and their performance scales well with large quantities of data.
+Inspired by success in speech recognition, some works \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} propose architectures based on long short-term memory networks (LSTMs) \cite{Hochreiter_Schmidhuber_1997}.
+Other works \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019} employ convolutional neural networks (CNNs) \cite{Krizhevsky_Sutskever_Hinton_2017} instead, which have been highly successful in computer vision tasks.
+Particularly, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures.
+Other works use neural architecture search (NAS) \cite{ahmadi2008modulation,dai2019multi,perenda2021evolutionary} to trade off performance with computational speed.
+Even though neural networks are currently the main and most effective method that tackles the AMC problem \cite{OShea_Roy_Clancy_2018}, they are very susceptible to adversarial perturbations, which compromises the security of the system against malicious attacks  \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}.
+\pf{that one can be shortened a bit if needed.}
+
+% With the emergence of deep learning \cite{goodfellow2016deep}, neural networks made their way into AMC, and are currently the main and most effective method that tackles this problem \cite{OShea_Roy_Clancy_2018}.
 Compared with previous methods, like feature extraction \cite{xie2008efficient,zhou2013design,zhang2017wireless} or maximum likelihood functions \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, neural networks are relatively fast, adaptable to any channel characteristics, and their performance scales well with high quantities of data.
@@
 %
-Recent studies have highlighted that the neural networks used in AMC are susceptible to adversarial attacks \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}, in which carefully crafted but almost imperceptible perturbations are added to the transmitted signal.
-These adversarial perturbations can be used as an effective way of jamming wireless communication systems, requiring much less energy and being stealthier than normal attacks.
-To craft them, algorithms like FGSM \cite{Goodfellow_Shlens_Szegedy_2015} or PGD \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} are typically used to solve the following optimization:
+Adversarial perturbations are carefully crafted but almost imperceptible disturbances that are added to the transmitted signal.
+These adversarial perturbations can be used as an effective way of jamming wireless communication systems as they require much less energy than normal attacks.
+Algorithms like FGSM \cite{Goodfellow_Shlens_Szegedy_2015} or PGD \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} can compute such perturbations by solving the following optimization problem:
 \begin{equation}
@@
 
-% Defenses. Relationship with data. Knowledge distillation
-Some defenses have been proposed to make networks more robust, like adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019}, but it comes at a cost in accuracy and computational time.
+Some defenses have been proposed to make models more robust against adversarial perturbations.
+Adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} has been shown to be effective in AMC \cite{maroto2021safeamc,manoj2022toward}.
+Randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have also been successful in making neural networks more robust.
+However, \pf{be clear on limitations of the above}.
 Some works have instead tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
-This is consistent with the increase in robustness when using knowledge distillation in combination with adversarial training~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits}, essentially training a student model with labels based on the teacher predictions.
+This is consistent with the increase in robustness that is observed when knowledge distillation is used in combination with adversarial training~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits}, which essentially consists in training a student model with labels based on the teacher predictions.
+\pf{if the above works do not play with KD in AMC, say it clearly} \pf{outline clearly the limitations of other KD works...}
+
+% % Defenses. Relationship with data. Knowledge distillation
+% Some defenses have been proposed to make networks more robust, like adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019}, but it comes at a cost in accuracy and computational time.
 
 % Our work, what are the main motivations. Contributions.
-In this work, we propose a data-centric approach with the purpose of making neural networks more accurate and robust to adversarial attacks.
-Motivated by the success of knowledge distillation, we propose to reduce the label noise in the training data by using the theoretical class probabilities, derived from the noise distribution of the channel with the maximum likelihood function.
-We show that neural networks trained with these probabilities perform better than if trained with the original labels, confirming the effect of label noise in robustness.
+In this work, we build on the above observations and propose a new data-centric method to make neural networks more accurate and robust to adversarial attacks.
+In particular, we propose to reduce the label noise \pf{is it formally noise?
+or uncertainties of some form?} in the training data by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation.
+We show that such knowledge distillation permits to achieve better accuracy than models trained with the original labels only.
+\pf{talk about the robustness aspects, and adversarial training, how is it performed} \pf{talk about robustness results} confirming the effect of label noise in robustness.
+\pf{recall benefits of the proposal, provide perspectives...
+how great is that?
+where do we go from there?}
 
-\section{Related Work}
+% \section{Related Work}
 
-% Maximum likelihood. 
-%   (More details can be found in "Survey of automatic modulation classification techniques").
-Maximum likelihood \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution for the AMC task.
+% % Maximum likelihood. 
+% %   (More details can be found in "Survey of automatic modulation classification techniques").
+% Maximum likelihood \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution for the AMC task.
 It computes the likelihood function of the received signal with all possible modulations and estimates the most likely modulation.
@@
 % Recent approaches. Explain and reference.
-Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC that avoids these shortcomings.
+% Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC that avoids these shortcomings.
 Inspired by success in speech recognition, some works \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} propose architectures based on long short-term memory networks (LSTMs) \cite{Hochreiter_Schmidhuber_1997}.
@@
 % Defenses to adversarial attacks
-Adversarial perturbations have been shown to fool neural networks in AMC \cite{Sadeghi_Larsson_2019,maroto2021benefits}.
+% Adversarial perturbations have been shown to fool neural networks in AMC \cite{Sadeghi_Larsson_2019,maroto2021benefits}.
 Unlike in other fields, in AMC the power of the perturbation is made dependent on the signal power with the signal-to-perturbation ratio (SPR).
@@
 % Knowledge distillation
+% Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance.
+However, these approaches do not help the student network in benefitting from the higher adversarial robustness that a teacher network could have~\cite{goldblum2020adversarially}.
+However, recently, there are works that have proposed alternative loss functions that address this problem~\cite{goldblum2020adversarially,zi2021revisiting,zhu2021reliable,shao2021and,maroto2022benefits}.
+These solutions encourage and improve the student robustness by matching its output with the teacher outputs on adversarial examples as well as clean examples.
+
+\section{Framework}
+
+\pf{Describe the settings, the different blocks, the AMC problem, the data/label issues in standard training}
+
+% -----
+
 Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance.
@@
 These solutions encourage and improve the student robustness by matching its output with the teacher outputs on adversarial examples as well as clean examples.
+\pf{to integrate in the part where KD would be introduced as a solution}
 
-\section{Maximum likelihood}
+%----
 
@@
 
-\section{Maximum likelihood distillation}
+\section{ML distillation for improved accuracy}
+
+\pf{ML estimation (offline), ML distillation ideas, KD-based model description + figure ideally}
+
+\subsection{Maximum likelihood distillation}
 
@@
 where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i)))$.
+
+\section{Robust model construction}
+
+\pf{introduce the problem of robustness, the adversarial training idea, the combination of KD and adversarial training, and provide a clear description of the robust model construction}
 
@@
 \section{Experiments}
+
+\pf{make sure that the technical aspects of the communication settings, are clear: non-coherence, type of channel, etc}
+
+\pf{maybe split clearly experiments into clear accuracy results and robustness results}
 
@@
 
-For future work, we think this methodology can be explored in other fields like physics, where neural networks are being increasingly preferred over mathematical models.
-Even in AMC, it could be interesting to explore other knowledge distillation losses and to use better ML functions that are adapted to Rayleigh or Rician channels, to improve the results when considering multiple types of channels.
+For future work, it could be interesting to explore other knowledge distillation losses and to use better ML functions that are adapted to Rayleigh or Rician channels, to improve the results when considering multiple types of channels.
+Our methodology can also be explored in other research fields like physics, where neural networks are being increasingly preferred over mathematical models \pf{be a bit more precise, or skip this last part...}
 

### 2022-10-14 paper/main.tex
Correct based on feedback

@@
 
-\title{Improving modulation classification by distilling maximum likelihood \pf{Maximum Likelihood Distillation for Robust Modulation Classification}
+\title{Maximum Likelihood Distillation for Robust Modulation Classification
 \thanks{This work has been sponsored by armasuisse Science and Technology under the project ARNO (project code ARAMIS 047-22).}
@@
 Those teach the model to be uncertain in challenging conditions, which permits to increase the standard accuracy, as well as the robustness of the model when combined with adversarial training.
-\pf{add some quantitative notes or more precise information about the actual results.}\pf{recall contributions/benefits or add general perspectives about the potential of the proposal: so what?
+Moreover, this increase in performance transfers to online settings, where the Maximum Likelihood function cannot be used in practice.
+In this work, we highlight the potential of learning to be uncertain in difficult scenarios, compared to directly removing label noise.
+%\pf{add some quantitative notes or more precise information about the actual results.}\pf{recall contributions/benefits or add general perspectives about the potential of the proposal: so what?
 why is that a cool idea, a cool paper?} \pf{re-check the full paragraph}
@@
 \begin{IEEEkeywords}
-Neural networks, robustness, Maximum Likelihood, knowledge distillation, automatic modulation classification
+Neural networks, Robustness, Maximum Likelihood, knowledge distillation, automatic modulation classification
 \end{IEEEkeywords}
@@
 Communication systems often require the receiver to recognize the modulation scheme that has been used to encode the transmitted signals.
-This is often refered as Automatic Modulation Classification (AMC) in applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
-The AMC task can be formaulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations.
+This is often referred as Automatic Modulation Classification (AMC) in applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
+The AMC task can be formulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations.
 Even if the solution is Bayes-optimal, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009} because ML requires prior knowledge of the channel characteristics and is computationally complex to solve in realtime.
@@
 Even though neural networks are currently the main and most effective method that tackles the AMC problem \cite{OShea_Roy_Clancy_2018}, they are very susceptible to adversarial perturbations, which compromises the security of the system against malicious attacks  \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}.
-\pf{that one can be shortened a bit if needed.}
+%\pf{that one can be shortened a bit if needed.}
 
@@
 
-Some defenses have been proposed to make models more robust against adversarial perturbations.
-Adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} has been shown to be effective in AMC \cite{maroto2021safeamc,manoj2022toward}.
-Randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have also been successful in making neural networks more robust.
-However, \pf{be clear on limitations of the above}.
-Some works have instead tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
-This is consistent with the increase in robustness that is observed when knowledge distillation is used in combination with adversarial training~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits}, which essentially consists in training a student model with labels based on the teacher predictions.
-\pf{if the above works do not play with KD in AMC, say it clearly} \pf{outline clearly the limitations of other KD works...}
+Some defenses have been proposed to make models more robust against adversarial perturbations in AMC.
+Particularly, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective.
+However, implementing these defenses comes at a significant cost in terms of computational complexity and they can greatly reduce the accuracy of the model.
+%\pf{be clear on limitations of the above}. 
+In contrast, some works from computer vision have tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
+Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} can reduce this effect by training a student model to match the outputs of a teacher model.
+While knowledge distillation has been used in AMC~\cite{ma2020cross}, some computer vision works~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits} have shown that to achieve adversarial robustness, the outputs of the student model have to be matched on adversarial examples as well.
+However, to achieve a significant increase in robustness, both the teacher and the student model have to be trained adversarially, which can be very costly computationally.
+%\pf{if the above works do not play with KD in AMC, say it clearly} \pf{outline clearly the limitations of other KD works...}
 
@@
 In this work, we build on the above observations and propose a new data-centric method to make neural networks more accurate and robust to adversarial attacks.
-In particular, we propose to reduce the label noise \pf{is it formally noise?
-or uncertainties of some form?} in the training data by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation.
-We show that such knowledge distillation permits to achieve better accuracy than models trained with the original labels only.
-\pf{talk about the robustness aspects, and adversarial training, how is it performed} \pf{talk about robustness results} confirming the effect of label noise in robustness.
-\pf{recall benefits of the proposal, provide perspectives...
+We think that the information given by the original labels is limited, not encoding the difference in uncertainty between low and high SNR signals.
+We propose to bring better information to the model
+%\pf{is it formally noise? or uncertainties of some form?} 
+by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation.
+We show that such knowledge distillation permits to achieve better accuracy and adversarial robustness, compared with using the original labels or removing label noise.
+We find similar increases in performance when we combine this approach with adversarial training, where we train the model to match the distilled labels on adversarial examples.
+We highlight that despite maximum likelihood being limited to offline settings, we see a clear benefit in the resulting model on online settings.
+We claim that helping the model be uncertain in challenging scenarios is a promising direction with relevance outside of AMC settings, further validating the intuition that the choice and the quality of the training data are highly influential on the adversarial robustness of the model.
+%\pf{talk about the robustness aspects, and adversarial training, how is it performed} \pf{talk about robustness results} \pf{recall benefits of the proposal, provide perspectives...
 how great is that?
@@
 
-% \section{Related Work}
-
-% % Maximum likelihood. 
-% %   (More details can be found in "Survey of automatic modulation classification techniques").
-% Maximum likelihood \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood} is the analytical solution for the AMC task.
-It computes the likelihood function of the received signal with all possible modulations and estimates the most likely modulation.
-Despite being Bayes-optimal, because it can be computationally expensive and requires prior knowledge of the channel characteristics, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009}.
-
-% Recent approaches. Explain and reference.
-% Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC that avoids these shortcomings.
-Inspired by success in speech recognition, some works \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} propose architectures based on long short-term memory networks (LSTMs) \cite{Hochreiter_Schmidhuber_1997}.
-Other works \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019} employ convolutional neural networks (CNNs) \cite{Krizhevsky_Sutskever_Hinton_2017} instead, which have been highly successful in computer vision tasks.
-Particularly, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures.
-Other works use neural architecture search (NAS) \cite{ahmadi2008modulation,dai2019multi,perenda2021evolutionary} to trade off performance with computational speed.
-However, all neural networks have common drawbacks: they are black-box models, less interpretable than their classical counterparts, and they are susceptible to adversarial perturbations, compromising the security of the system against malicious attacks.
-
-% Defenses to adversarial attacks
-% Adversarial perturbations have been shown to fool neural networks in AMC \cite{Sadeghi_Larsson_2019,maroto2021benefits}.
-Unlike in other fields, in AMC the power of the perturbation is made dependent on the signal power with the signal-to-perturbation ratio (SPR).
-Some defenses have been proposed to make models more robust against adversarial perturbations.
-Adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} has been shown to be effective in AMC \cite{maroto2021safeamc,manoj2022toward}.
-Randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have also been successful in making neural networks more robust.
-
-% Knowledge distillation
-% Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance.
-However, these approaches do not help the student network in benefitting from the higher adversarial robustness that a teacher network could have~\cite{goldblum2020adversarially}.
-However, recently, there are works that have proposed alternative loss functions that address this problem~\cite{goldblum2020adversarially,zi2021revisiting,zhu2021reliable,shao2021and,maroto2022benefits}.
-These solutions encourage and improve the student robustness by matching its output with the teacher outputs on adversarial examples as well as clean examples.
-
 \section{Framework}
 
-\pf{Describe the settings, the different blocks, the AMC problem, the data/label issues in standard training}
+%\pf{Describe the settings, the different blocks, the AMC problem, the data/label issues in standard training}
 
-% -----
+The communication system that characterizes the AMC task is shown in Figure \ref{fig:comm_system} with the gray blocks.
+It is composed of the transmitter, the communication channel, and the receptor.
+The transmitter is composed of a modulator and a communication filter $r'(x)$.
+The modulator uses a specific mapping to convert the data into a sequence of symbols.
+The symbols are upsampled and passed through the communication filter (e.g.
+root-raised cosine) to avoid inter-symbol interference (ISI).
+The signal is transmitted through the communication channel, which inevitably adds noise and distortion to the signal.
+The receptor receives that signal, and it is composed of another communication filter $r(x)$, that downsamples and transforms the signal back into symbols, and the demodulator, which converts the symbols into data.
 
-Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} consists in training a student model to match the outputs of a teacher model, which has been shown to be effective in transferring performance.
-However, these approaches do not help the student network in benefitting from the higher adversarial robustness that a teacher network could have~\cite{goldblum2020adversarially}.
-However, recently, there are works that have proposed alternative loss functions that address this problem~\cite{goldblum2020adversarially,zi2021revisiting,zhu2021reliable,shao2021and,maroto2022benefits}.
-These solutions encourage and improve the student robustness by matching its output with the teacher outputs on adversarial examples as well as clean examples.
-\pf{to integrate in the part where KD would be introduced as a solution}
+Automatically choosing the correct demodulator based on the signal received is the problem AMC tries to solve. 
+In practice, we distinguish between two scenarios: the coherent scenario, where we have complete knowledge of the system and it is only assumed in offline settings, and the non-coherent scenario, where some or all the channel and transmitter characteristics are unknown.
+The latter is generally used in online settings and to test the model effectiveness in real conditions.
 
-%----
-
-Normally, to perform well on AMC, neural networks are trained to infer the modulation used in transmission from the signal received.
+%Normally, to perform well on AMC, neural networks are trained to infer the modulation used in transmission from the signal received.
 Thus, the network will be optimized to be as confident and accurate as possible on the training set.
@@
 Such cases are numerous when testing models in the AMC literature, where the signal received could have been generated from any of multiple modulations with similar probability.
-
-While in many other tasks, these probabilities would be difficult or impossible to obtain, in AMC, we can use the maximum likelihood (ML) function to derive the real probabilities.
-Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
-Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and given the received symbols $r(x)$, where $r$ applies the proper communication filter and downsampling to the received signal.
-We show in Figure \ref{fig:comm_system} a diagram describing the communication system.
-We highlight that while the neural network has to process directly what the receptor receives, maximum likelihood processes the symbols of that signal instead.
-This is possible because we can assume we know the communication filter and upsampling used in the transmitter, which we can invert at the receptor.
-The ML function when the channel is gaussian is given by the following expression
-\begin{equation}
-	f_{i}(r(x)) = \dfrac{1}{2\pi \sigma^{2}|M_i|}\prod_{t=1}^{T} \sum_{j=1}^{|M_i|} \exp\left(-\dfrac{\lVert r(x)_t - s_j\rVert^{2}}{2 \sigma^{2}}\right)
-\label{eq:ml}
-\end{equation}
-where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that correspond to the state $j$.
-Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$.
+When training neural networks to perform well in AMC or any other task, they are optimized to be as confident and accurate as possible on a given training set.
+In the case of AMC, the set is composed of the received signals and their corresponding labels describing the modulation used in the form of one hot encoded vectors.
+Our claim is that these labels are not good enough to train the model in the AMC task.
+The reason is that for noisier and heavily distorted signals, there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict.
+Such cases are numerous when testing models in the AMC literature.
+Thus, to properly distinguish between cleaner and noisier signals, we want to give the model more information that conveys the fact that there are signals where it should not be confident in its prediction.
+Luckily, in AMC there is an analytical model that is able to measure this uncertainty in coherent scenarios: the Maximum likelihood function.
 
@@
 \end{tikzpicture}
-\caption{Simplified diagram of the communication system.
-The transmitter sends the binary data using the modulator, which converts the data into symbols, and $r'(x)$, which upsamples the signal and passes it through a communication filter (e.g.
-root raised cosine).
-The signal passes through the communication channel, which adds noise and distortion to the signal.
-The receptor does the inverse operation and demodulates the signal based on the neural network prediction.
-As shown, the signals used by the neural network and ML are slightly different.}
+\caption{Simplified diagram of the communication system. The ML function takes the signal symbols as its input instead of the received signal itself.}
 \label{fig:comm_system}
 \end{figure}
+
+\section{ML distillation for improved accuracy}
+
+%\pf{ML estimation (offline), ML distillation ideas, KD-based model description + figure ideally}
+
+\subsection{Maximum likelihood function}
+
+%In many other tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class.
+However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities.
+Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
+Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and given the received symbols $r(x)$, where $r$ applies the proper communication filter and downsampling to the received signal.
+We show in Figure \ref{fig:comm_system} a diagram describing the communication system.
+We highlight that while the neural network has to process directly what the receptor receives, maximum likelihood processes the symbols of that signal instead.
+This is possible because we can assume we know the communication filter and upsampling used in the transmitter, which we can invert at the receptor.
+The ML function when the channel is gaussian is given by the following expression
+In many other tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class.
+However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities.
+Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
+Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and that we know the proper communication filter $r(\cdot)$ that matches the filter $r'(\cdot)$ used in transmission, then the ML function is given by the following expression
+\begin{equation}
+	f_{i}(r(x)) = \dfrac{1}{2\pi \sigma^{2}|M_i|}\prod_{t=1}^{T} \sum_{j=1}^{|M_i|} \exp\left(-\dfrac{\lVert r(x)_t - s_j\rVert^{2}}{2 \sigma^{2}}\right)
+\label{eq:ml}
+\end{equation}
+where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $x$ is the received signal before the communication filter, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that correspond to the state $j$.
+Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$.
+Note that the ML function directly processes $r(x)$ instead of $x$, as shown in Figure \ref{fig:comm_system}.
 
@@
 Based on these limitations, we propose a hybrid approach.
-We will use a neural network for inference, but we will train it with the probabilities given by maximum likelihood.
-Because Equation \ref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities.
+We will use a neural network for inference, but we will train it with the probabilities given by ML, to give the model this additional uncertainty information.
+Because \eqref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities.
 This is feasible when we consider that we can have full knowledge of the channel conditions by generating the training samples ourselves.
-Moreover, after training the neural network, ML is no longer needed.
-Thus allowing our model to be usable under unknown channel conditions, which is typical in real AMC scenarios.
+Moreover, after training the neural network, ML is no longer needed, enabling our model to be used in non-coherent scenarios, which model real communication systems.
 
-\section{ML distillation for improved accuracy}
+\subsection{Our proposed distillation}
 
-\pf{ML estimation (offline), ML distillation ideas, KD-based model description + figure ideally}
-
-\subsection{Maximum likelihood distillation}
-
-Typically in AMC, neural networks try to fit a function that takes as input the received signal data and outputs the modulation used by the transmitter.
+%Typically in AMC, neural networks try to fit a function that takes as input the received signal data and outputs the modulation used by the transmitter.
 Thus, the corresponding loss that the model uses to train is given by the standard training loss
+In the AMC literature, neural networks are generally trained with the standard training (ST) loss
 \begin{equation}
@@
 
-However, in practice, the neural network is trained with noisy signals where the modulation that was used cannot be inferred so easily.
+%However, in practice, the neural network is trained with noisy signals where the modulation that was used cannot be inferred so easily.
 Intuitively, for these signals we would like the outputs of the network to rely on this sense of uncertainty.
 Thus, with similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in the corresponding coherent scenario.
+However, our proposal is to give the model labels that better express the uncertainty of highly corrupted signals.
+Thus, using similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in its corresponding coherent scenario.
 \begin{equation}
@@
 \end{equation}
-where $p_{ML}$ is the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal.
+where $p_{ML}$ gives the class probabilities from applying the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal.
 Because $r$ and $p_{ML}$ are functions that depend on information that is not known in non-coherent scenarios, we propose to use this loss function only when training the network, where this information can be known.
@@
 The main downside of using this function is that, while the probabilities given by ML are optimal in the context of a coherent scenario, they differ from the real probabilities $p^{*}$ that are conditional to the channel and communication filter distributions, $H$.
-However, our hypothesis, which we test in the following Section, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which enforce full confidence on all samples, no matter how noisy they are.
+However, our hypothesis, which we test in Section \ref{sec:experiments}, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which enforce full confidence on all samples, no matter how noisy they are.
 Mathematically, these probabilities are related by the following expression:
@@
 Intuitively, training on these signals will potentially confuse the network.
-Thus, we will use standard training loss but removing the label noise by training only on the signals where this does not happen:
+Thus, we will use the standard training loss but training only on the signals without label noise:
 \begin{equation}
@@
 
-\pf{introduce the problem of robustness, the adversarial training idea, the combination of KD and adversarial training, and provide a clear description of the robust model construction}
+%\pf{introduce the problem of robustness, the adversarial training idea, the combination of KD and adversarial training, and provide a clear description of the robust model construction}
 
-While the previous proposals are effective in incorporating the ML information to train the model, they do not address directly the vulnerability of neural networks to adversarial perturbations.
-One of the most straightforward ways to improve the network robustness is to use the adversarial training loss function
+There are multiple reasons why we want neural networks to be robust against adversarial perturbations.
+Not only it enables secure systems against adversarial attacks, but robust models are also more interpretable, basing their decisions on sensible features for the AMC task, like the quadrature and in phase components of the symbols \cite{maroto2021safeamc}.
+One of the most straightforward ways to improve the network robustness is to use the adversarial training (AT) loss function
 \begin{equation}
@@
 where $x_i' = x_i + \delta_i^*$ is a crafted adversarial signal that maximizes the cross-entropy loss of the neural network in the neighborhood of $x_i$.
+Because the adversarial perturbation is dependent on the model weights, it has to be computed at each training iteration, typically using PGD.
 
-Analogously to Equation \ref{eq:st_ml}, we propose the following loss to match the model to the ML probabilities
+Analogously to \eqref{eq:st_ml}, we propose the following loss, in which the original labels are replaced with the ML probabilities:
 \begin{equation}
@@
 \end{equation}
-We highlight that, unlike the analogous standard training function, we have to make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.
-This assumption holds when the adversarial perturbation is sufficiently small, which is normally the case during adversarial training.
+We highlight that the ML function assumes the signal was distorted with gaussian noise, which is no longer since the input was adversarially perturbed.
+However, during adversarial training the adversarial perturbation used is very small, so we can make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.
 
@@
 
-For training with non-gaussian channels, because we remove the Rayleigh/Rician components, we have the drawback that we cannot directly translate the adversarial perturbation added to the neural network to the signal received by ML.
-For that reason, we have considered the following two solutions: to use the ML probabilities of the uncorrupted signal as follows
+For training with non-gaussian channels, because we remove the Rayleigh/Rician components for the ML function, we have the drawback that we cannot directly translate the adversarial perturbation added to the neural network to the signal received by ML.
+For that reason, we have considered the following two solutions: to use the ML probabilities of the uncorrupted signal
 \begin{equation}
@@
 \end{equation}
-and to recompute the adversarial perturbation but for the ML function using the following loss function
+and to use the adversarial example given by the ML function
 \begin{equation}
@@
 \end{equation}
-where $g_i$ is the received signal when the Rayleigh/Rician effects are removed and $r(g_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of ML in the neighborhood of $r(g_i)$.
-
-We will show that adversarial perturbations change greatly the probabilities of the received signal, making it desirable to use AT\_AML over AT\_NML.
+where $g_i$ is the received signal after removing the Rayleigh/Rician components, and $r(g_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of ML in the neighborhood of $r(g_i)$.
+Because adversarial attacks can significantly change the probabilities of the received signal, we recommend to use AT\_AML over AT\_NML.
 
 \section{Experiments}
+\label{sec:experiments}
 
-\pf{make sure that the technical aspects of the communication settings, are clear: non-coherence, type of channel, etc}
+%\pf{make sure that the technical aspects of the communication settings, are clear: non-coherence, type of channel, etc}
 
-\pf{maybe split clearly experiments into clear accuracy results and robustness results}
+%\pf{maybe split clearly experiments into clear accuracy results and robustness results}
 
@@
 For the transmitter, we use 8 samples per symbol and a root raised cosine filter with rolloff 0.35.
-Table \ref{tab:sbasic} proves that the network is much more effective when we remove the label noise, both in the standard and adversarial training scenarios.
-The increase in robustness is much more significant, which confirms our expectations.
-However, when using the ML probabilities, we get the biggest increase in performance, which underlines the benefit of distinguishing between uncertain and certain predictions.
+Table \ref{tab:sbasic} shows that the network is much more robust when we remove the label noise, both in the standard and adversarial training scenarios, as we would expect from previous intuitions.
+However, when using the ML probabilities, we get the biggest increase in performance, which underlines the benefit of learning this additional uncertainty information.
 
@@
 Table \ref{tab:sawgn2p} shows very similar results as the previous case.
-However, since there are more parameter configurations, the difference between $p_{ML}$ and $p^{*}$ increases, which shows in the lower increase in performance between LNR and ML methodologies overall.
+However, since there are more parameter configurations, the difference between $p_{ML}$ and $p^{*}$ increases, which shows in the lower increase in performance between LNR and ML approaches.
 
@@
 For future work, it could be interesting to explore other knowledge distillation losses and to use better ML functions that are adapted to Rayleigh or Rician channels, to improve the results when considering multiple types of channels.
-Our methodology can also be explored in other research fields like physics, where neural networks are being increasingly preferred over mathematical models \pf{be a bit more precise, or skip this last part...}
+%Our methodology can also be explored in other research fields like physics, where neural networks are being increasingly preferred over mathematical models \pf{be a bit more precise, or skip this last part...}
 

### 2022-10-22 paper/main.tex
Add clement feedback

@@
 We then propose to use the Maximum Likelihood function, which could solve the AMC problem in offline settings, to generate better training labels.
-Those teach the model to be uncertain in challenging conditions, which permits to increase the standard accuracy, as well as the robustness of the model when combined with adversarial training.
-Moreover, this increase in performance transfers to online settings, where the Maximum Likelihood function cannot be used in practice.
-In this work, we highlight the potential of learning to be uncertain in difficult scenarios, compared to directly removing label noise.
+Those labels teach the model to be uncertain in challenging conditions, which permits to increase the accuracy, as well as the robustness of the model when combined with adversarial training.
+Interestingly, we observe that this increase in performance transfers to online settings, where the Maximum Likelihood function cannot be used in practice.
+Overall, this work highlights the potential of learning to be uncertain in difficult scenarios, compared to directly removing label noise.
 %\pf{add some quantitative notes or more precise information about the actual results.}\pf{recall contributions/benefits or add general perspectives about the potential of the proposal: so what?
@@
 Communication systems often require the receiver to recognize the modulation scheme that has been used to encode the transmitted signals.
-This is often referred as Automatic Modulation Classification (AMC) in applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
+The task is often referred to as Automatic Modulation Classification (AMC) and has applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications.
 The AMC task can be formulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations.
@@
 Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC as neural networks are relatively fast at inference time, adaptable to any channel characteristics, and their performance scales well with large quantities of data.
-Inspired by success in speech recognition, some works \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} propose architectures based on long short-term memory networks (LSTMs) \cite{Hochreiter_Schmidhuber_1997}.
-Other works \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019} employ convolutional neural networks (CNNs) \cite{Krizhevsky_Sutskever_Hinton_2017} instead, which have been highly successful in computer vision tasks.
+Two classes of architectures have been proposed for this task: long short-term memory networks (LSTMs) \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} and convolutional neural networks (CNNs) \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019}.
 Particularly, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures.
@@
 
-Some defenses have been proposed to make models more robust against adversarial perturbations in AMC.
-Particularly, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective.
-However, implementing these defenses comes at a significant cost in terms of computational complexity and they can greatly reduce the accuracy of the model.
+Among the defenses proposed to increase the adversarial robustness of AMC models, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective.
+But, in addition to being computationally costly, these defenses greatly reduce the accuracy of the model on clean data.
 %\pf{be clear on limitations of the above}.
+
 In contrast, some works from computer vision have tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
@@
 In this work, we build on the above observations and propose a new data-centric method to make neural networks more accurate and robust to adversarial attacks.
-We think that the information given by the original labels is limited, not encoding the difference in uncertainty between low and high SNR signals.
-We propose to bring better information to the model
+We make the hypothesis that the information given by the original labels is limited, and does not encode the difference in uncertainty between low and high SNR signals.
+Therefore, we propose to bring better information to the model
 %\pf{is it formally noise? or uncertainties of some form?} 

### 2022-10-25 paper/main.tex
Add Pascal final feedback

@@
 Overall, this work highlights the potential of learning to be uncertain in difficult scenarios, compared to directly removing label noise.
-%\pf{add some quantitative notes or more precise information about the actual results.}\pf{recall contributions/benefits or add general perspectives about the potential of the proposal: so what?
-why is that a cool idea, a cool paper?} \pf{re-check the full paragraph}
+%TODO: clear enough at this stage?
 \end{abstract}
@@
 The AMC task can be formulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations.
-Even if the solution is Bayes-optimal, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009} because ML requires prior knowledge of the channel characteristics and is computationally complex to solve in realtime.
+Even if this solution is Bayes-optimal, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009} because ML requires prior knowledge of the channel characteristics and is computationally complex to solve in realtime.
 
 Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC as neural networks are relatively fast at inference time, adaptable to any channel characteristics, and their performance scales well with large quantities of data.
-Two classes of architectures have been proposed for this task: long short-term memory networks (LSTMs) \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} and convolutional neural networks (CNNs) \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019}.
-Particularly, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures.
+Two classes of neural network architectures have been proposed for this task: long short-term memory networks (LSTMs) \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} and convolutional neural networks (CNNs) \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019}.
+In particular, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures.
 Other works use neural architecture search (NAS) \cite{ahmadi2008modulation,dai2019multi,perenda2021evolutionary} to trade off performance with computational speed.
-Even though neural networks are currently the main and most effective method that tackles the AMC problem \cite{OShea_Roy_Clancy_2018}, they are very susceptible to adversarial perturbations, which compromises the security of the system against malicious attacks  \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}.
+Even though neural networks currently represent the main and most effective method to tackle the AMC problem \cite{OShea_Roy_Clancy_2018}, they are very susceptible to adversarial perturbations, which compromises the security of the system against malicious attacks  \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}.
 %\pf{that one can be shortened a bit if needed.}
@@
 % Effect of adversarial perturbations.
-% TODO: maybe add motivation of why robust models are important
-%
 Adversarial perturbations are carefully crafted but almost imperceptible disturbances that are added to the transmitted signal.
@@
 where $\delta_i^*$ is the adversarial perturbation added to the received signal $x_i$, $y_i$ is the one-hot-encoded vector of length K that encodes the modulation used, $\Ls$ is the cross-entropy loss, $f_{\theta}$ is the neural network defined with weights $\theta$, and $\varepsilon$ is a fixed value that constrains the norm of the perturbation to be small and imperceptible.
-
-Among the defenses proposed to increase the adversarial robustness of AMC models, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective.
+On the other hand, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective in increasing the robustness of AMC models.
 But, in addition to being computationally costly, these defenses greatly reduce the accuracy of the model on clean data.
@@
 
-In contrast, some works from computer vision have tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
+Some works from computer vision have tried to understand why networks are so susceptible to attacks, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}.
 Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} can reduce this effect by training a student model to match the outputs of a teacher model.
 While knowledge distillation has been used in AMC~\cite{ma2020cross}, some computer vision works~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits} have shown that to achieve adversarial robustness, the outputs of the student model have to be matched on adversarial examples as well.
-However, to achieve a significant increase in robustness, both the teacher and the student model have to be trained adversarially, which can be very costly computationally.
-%\pf{if the above works do not play with KD in AMC, say it clearly} \pf{outline clearly the limitations of other KD works...}
-
-% % Defenses. Relationship with data. Knowledge distillation
-% Some defenses have been proposed to make networks more robust, like adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019}, but it comes at a cost in accuracy and computational time.
+And, to achieve a significant increase in robustness, both the teacher and the student models have to be trained adversarially, which can be very costly computationally.
 
@@
 We make the hypothesis that the information given by the original labels is limited, and does not encode the difference in uncertainty between low and high SNR signals.
-Therefore, we propose to bring better information to the model
-%\pf{is it formally noise? or uncertainties of some form?} 
-by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation.
-We show that such knowledge distillation permits to achieve better accuracy and adversarial robustness, compared with using the original labels or removing label noise.
-We find similar increases in performance when we combine this approach with adversarial training, where we train the model to match the distilled labels on adversarial examples.
-We highlight that despite maximum likelihood being limited to offline settings, we see a clear benefit in the resulting model on online settings.
+%TODO: contributions, models
+Therefore, we propose to bring better information to the model by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation. 
+%TODO: + add a couple of sentences about the selection/the proposed model + talk about adversarial training part
+We show experimentally that such knowledge distillation permits to achieve better accuracy and adversarial robustness, compared with using the original labels or removing label noise. 
+%TODO: explain results
+Then, we show similar increases in performance when we combine this approach with adversarial training, where we train the model to match the distilled labels on adversarial examples.
+We highlight, that despite maximum likelihood being limited to offline settings, we see a clear benefit in the resulting model even in online settings.
 We claim that helping the model be uncertain in challenging scenarios is a promising direction with relevance outside of AMC settings, further validating the intuition that the choice and the quality of the training data are highly influential on the adversarial robustness of the model.
@@
 The modulator uses a specific mapping to convert the data into a sequence of symbols.
-The symbols are upsampled and passed through the communication filter (e.g.
-root-raised cosine) to avoid inter-symbol interference (ISI).
+The symbols are upsampled and passed through the communication filter (e.g., root-raised cosine) to avoid inter-symbol interference (ISI).
 The signal is transmitted through the communication channel, which inevitably adds noise and distortion to the signal.
-The receptor receives that signal, and it is composed of another communication filter $r(x)$, that downsamples and transforms the signal back into symbols, and the demodulator, which converts the symbols into data.
+The receptor is composed of another communication filter $r(x)$, that downsamples and transforms the signal back into symbols, and the demodulator, which converts the symbols into data.
 
-Automatically choosing the correct demodulator based on the signal received is the problem AMC tries to solve. 
-In practice, we distinguish between two scenarios: the coherent scenario, where we have complete knowledge of the system and it is only assumed in offline settings, and the non-coherent scenario, where some or all the channel and transmitter characteristics are unknown.
-The latter is generally used in online settings and to test the model effectiveness in real conditions.
+Automatically choosing the correct demodulator based on the signal received is the problem that AMC tries to solve. 
+In practice, we distinguish between two scenarios: the coherent scenario, where we have complete knowledge of the system and it is only valid in offline settings; and the non-coherent scenario, where some or all the channel and transmitter characteristics are unknown.
+The latter is generally used in online settings, as well as to test the model effectiveness in real conditions.
 
-%Normally, to perform well on AMC, neural networks are trained to infer the modulation used in transmission from the signal received.
-Thus, the network will be optimized to be as confident and accurate as possible on the training set.
-However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals typically there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict.
-Such cases are numerous when testing models in the AMC literature, where the signal received could have been generated from any of multiple modulations with similar probability.
-When training neural networks to perform well in AMC or any other task, they are optimized to be as confident and accurate as possible on a given training set.
-In the case of AMC, the set is composed of the received signals and their corresponding labels describing the modulation used in the form of one hot encoded vectors.
+When training neural networks to perform well in AMC or any other task, one optimizes them to be as confident and accurate as possible on a given training set.
+In the case of AMC, that set is composed of the received signals and their corresponding labels describing the modulation used in the form of one hot encoded vectors.
 Our claim is that these labels are not good enough to train the model in the AMC task.
@@
 Such cases are numerous when testing models in the AMC literature.
-Thus, to properly distinguish between cleaner and noisier signals, we want to give the model more information that conveys the fact that there are signals where it should not be confident in its prediction.
-Luckily, in AMC there is an analytical model that is able to measure this uncertainty in coherent scenarios: the Maximum likelihood function.
+Therefore, we want train our model with better information so that it can express this uncertainty with less confident predictions.
+Luckily, in AMC, there is an analytical model that can give us the probability vectors needed to train the model: the Maximum likelihood function.
 
@@
 
-%In many other tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class.
+In many tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class.
 However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities.
 Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
-Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and given the received symbols $r(x)$, where $r$ applies the proper communication filter and downsampling to the received signal.
-We show in Figure \ref{fig:comm_system} a diagram describing the communication system.
-We highlight that while the neural network has to process directly what the receptor receives, maximum likelihood processes the symbols of that signal instead.
-This is possible because we can assume we know the communication filter and upsampling used in the transmitter, which we can invert at the receptor.
-The ML function when the channel is gaussian is given by the following expression
-In many other tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class.
-However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities.
-Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions.
-Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and that we know the proper communication filter $r(\cdot)$ that matches the filter $r'(\cdot)$ used in transmission, then the ML function is given by the following expression
+Particularly, if we assume that the channel is gaussian with variance $\sigma^{2}$, and that we know the proper communication filter $r(\cdot)$ that matches the filter $r'(\cdot)$ used in transmission, then the ML function is given by the following expression
 \begin{equation}
@@
 \end{equation}
-where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $x$ is the received signal before the communication filter, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that correspond to the state $j$.
+where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $x$ is the received signal before the communication filter, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that corresponds to the state $j$.
 Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$.
@@
 
-The reason why ML is not preferred over neural networks is simple: they perform badly in non-coherent scenarios, where the channel or transmission filter parameters are unknown.
+The reason why ML is not used in practice is simple: they perform badly in non-coherent scenarios, where the channel or transmission filter parameters are unknown.
 Moreover, any small deviation from the real channel parameters has a major effect on the ML performance, which discards the possibility of trying to estimate these parameters.
-Moreover, incorporating the parameter uncertainty in the ML formulation makes it much more costly computationally without being more performant than neural networks.
+Finally, incorporating the parameter uncertainty in the ML formulation makes it much more costly computationally, without being more performant than neural networks.
 
 Based on these limitations, we propose a hybrid approach.
-We will use a neural network for inference, but we will train it with the probabilities given by ML, to give the model this additional uncertainty information.
-Because \eqref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities.
+We will use a neural network for inference, but we will train it with the probabilities computed offline with ML, to give the model this additional uncertainty information.
+Because Eq.
+\eqref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities.
 This is feasible when we consider that we can have full knowledge of the channel conditions by generating the training samples ourselves.
-Moreover, after training the neural network, ML is no longer needed, enabling our model to be used in non-coherent scenarios, which model real communication systems.
+Moreover, after training the neural network, ML is no longer needed, so that our model can be used in non-coherent scenarios, which correspond to real communication systems.
 
@@
 
-%Typically in AMC, neural networks try to fit a function that takes as input the received signal data and outputs the modulation used by the transmitter.
-Thus, the corresponding loss that the model uses to train is given by the standard training loss
 In the AMC literature, neural networks are generally trained with the standard training (ST) loss
@@
 
-%However, in practice, the neural network is trained with noisy signals where the modulation that was used cannot be inferred so easily.
-Intuitively, for these signals we would like the outputs of the network to rely on this sense of uncertainty.
-Thus, with similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in the corresponding coherent scenario.
-However, our proposal is to give the model labels that better express the uncertainty of highly corrupted signals.
+However, our proposal is to provide the model with labels that better express the uncertainty of highly corrupted signals.
 Thus, using similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in its corresponding coherent scenario.
@@
 The main downside of using this function is that, while the probabilities given by ML are optimal in the context of a coherent scenario, they differ from the real probabilities $p^{*}$ that are conditional to the channel and communication filter distributions, $H$.
-However, our hypothesis, which we test in Section \ref{sec:experiments}, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which enforce full confidence on all samples, no matter how noisy they are.
+However, our hypothesis, which we test in Section \ref{sec:experiments}, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which rather enforce full confidence on all samples, no matter how noisy they are.
 Mathematically, these probabilities are related by the following expression:
@@
 \end{equation}
-where $m$ is the vector of all modulations, $h_i$ is one of the possible coherent scenarios where the true coherent scenario is assigned to $h_0$ without loss of generality.
+where $m$ is the vector of all modulations, $h_i$ is one possible choice of channel and transmitter parameters.
 Thus, $p[m|x] = p^{*}$ and $p_{ML} = p[m|x,H=h_0]$.
-Based on this formulation, our model will match better $p^{*}$ when the true communication parameters $H=h_0$ can be easily predicted from x ($p[H=h_0|x] \approx 1$) or when the communication parameters do not affect that much the probabilities ($p[m|x,H=h_i] \approx p_{ML} \; \forall i$).
+Based on this formulation, our model will match better $p^{*}$ when the true communication parameters $H=h_0$ can be easily predicted from x ($p[H=h_0|x] \approx 1$) or when the communication parameters do not affect that much the probabilities ($p[m|x,H=h_i] \approx p_{ML}, \; \forall i$).
 
@@
 where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i)))$.
+%TODO: motivate/explain. Why you have two solutions, and clearly say if they are fully independent.
 
@@
 
-There are multiple reasons why we want neural networks to be robust against adversarial perturbations.
-Not only it enables secure systems against adversarial attacks, but robust models are also more interpretable, basing their decisions on sensible features for the AMC task, like the quadrature and in phase components of the symbols \cite{maroto2021safeamc}.
+Robust models offer more security against adversarial attacks, but they are also more interpretable, basing their decisions on sensible features for the AMC task, like the quadrature and in phase components of the symbols \cite{maroto2021safeamc}.
 One of the most straightforward ways to improve the network robustness is to use the adversarial training (AT) loss function
@@
 
-Analogously to \eqref{eq:st_ml}, we propose the following loss, in which the original labels are replaced with the ML probabilities:
+Analogously to Eq. \eqref{eq:st_ml}, we propose the following adversarial loss, in which the original labels are replaced with the ML probabilities:
 \begin{equation}
@@
 \end{equation}
-We highlight that the ML function assumes the signal was distorted with gaussian noise, which is no longer since the input was adversarially perturbed.
-However, during adversarial training the adversarial perturbation used is very small, so we can make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.
+We highlight that the ML function assumes that the signal is distorted with gaussian noise, which is not accurate since the input was adversarially perturbed.
+However, during adversarial training the adversarial perturbation typically is very small, so we can make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.
 
-One way to reduce the effect of this assumption is to instead remove label noise using ML
+One way to reduce the effect of this assumption is to instead remove the label noise using ML
 \begin{equation}
@@
 where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i')))$. 
+% TODO: clarify flow of ideas!
 Even if $p_{ML}$ is not strictly correct due to the adversarial perturbation being relatively large, it will tend to remove signals that are already very noisy, thus greatly reducing the chance of label noise affecting adversarial training.
 Since label noise has a direct impact on the robustness of the network, we expect label noise removal to be particularly effective.
+% TODO: the structure of ideas, and why you propose AT, then AT_ML, then AT_LNR, is not clear: motivate + explain what is the final proposal and why
 
+% TODO: not clear!
 For training with non-gaussian channels, because we remove the Rayleigh/Rician components for the ML function, we have the drawback that we cannot directly translate the adversarial perturbation added to the neural network to the signal received by ML.
@@
 where $g_i$ is the received signal after removing the Rayleigh/Rician components, and $r(g_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of ML in the neighborhood of $r(g_i)$.
-Because adversarial attacks can significantly change the probabilities of the received signal, we recommend to use AT\_AML over AT\_NML.
+Because adversarial attacks can significantly change the probabilities of the received signal, we always recommend to use AT\_AML over AT\_NML.
+%TODO: again, not very clear about what is the final propsal and why? in what settings?
 
@@
 
-We propose to evaluate our methodology on scenarios with different levels of non-coherence.
+We propose to evaluate our proposal on scenarios with different levels of non-coherence in the wireless channel.
 This way, we can verify if the probabilities generated by ML in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions.
@@
 For all the experiments, we train the neural network to distinguish between the following digital modulations: BPSK, QPSK, 8/16/32/64/128/256-PSK, PAM4, 16/32/64/128/256-QAM, GFSK, CPFSK, B-FM, DSB-AM, SSB-AM, and OQPSK \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020}.
-For the last six modulations, the ML formulation cannot be directly applied, so we use the original labels $y$ on these cases.
+For the last six modulations, the ML formulation cannot be directly applied since they shift the signal frequency, phase or amplitude to represent different states, so we use the original labels $y$ on these cases.
+% TODO: but then, why do you even consider those cases?
 For all settings, we consider that the signal sampling frequency is 200KHz.
@@
 The duration of the signal is set to 1024 samples, for consistency with other similar datasets \cite{OShea_West_2016}.
-For the network, we use a ResNet-based network architecture \cite{OShea_Roy_Clancy_2018}, that while being fast to train has great performance in AMC.
+For the network, we use a ResNet-based network architecture \cite{OShea_Roy_Clancy_2018}, which trains fast and has great performance in AMC.
 We train the network for 100 epochs using SGD optimization with momentum 0.9 and learning rate 0.01, decaying exponentially at a rate of 0.95 per epoch.
 We use gradient clipping of size 5 and weight decay of 5e-4.
-When computing the adversarial perturbations for both training and testing the robustness of the network, we use PGD-7 with $\varepsilon=20 \text{dB SPR}$ (signal-to-perturbation ratio).
+When computing the adversarial perturbations for both training and testing the robustness of the network, we use PGD-7 \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} with $\varepsilon=20 \text{dB SPR}$ (signal-to-perturbation ratio).
 
@@
 Table \ref{tab:sbasic} shows that the network is much more robust when we remove the label noise, both in the standard and adversarial training scenarios, as we would expect from previous intuitions.
-However, when using the ML probabilities, we get the biggest increase in performance, which underlines the benefit of learning this additional uncertainty information.
+However, when using the ML probabilities, we get the biggest increase in performance, which underlines the benefit of learning with this additional uncertainty information.
 
@@
 Table \ref{tab:sawgn2p} shows very similar results as the previous case.
-However, since there are more parameter configurations, the difference between $p_{ML}$ and $p^{*}$ increases, which shows in the lower increase in performance between LNR and ML approaches.
+However, since there are more parameter configurations, the difference between $p_{ML}$ and $p^{*}$ increases, which reflects in the lower increase in performance between LNR and ML approaches.
 
 For the third and final scenario, we use the transmitter settings of the first scenario, but we consider also Rician and Rayleigh channels with AWGN noise.
-Table \ref{tab:sp0c20} shows smaller improvements compared to the two previous cases.
+Table \ref{tab:sp0c20} shows smaller improvements of our method compared to the two previous experimental cases.
 While the probabilities of ML are not discerning well the label noise, which shows in the lack of improvement for the LNR methods, they can still help the network as seen in the ML methods.
-We highlight that for adversarial training is much more preferable to perturb the signal received by ML before computing the probabilities, due to these probabilities being much more representative of the signal used by the model than the probabilities in the unperturbed point.
+We highlight that, for adversarial training,
+% TODO: not clear/rephrase
+it is much more preferable to perturb the signal received by ML before computing the probabilities, due to these probabilities being much more representative of the signal used by the model than the probabilities in the unperturbed point.
+
+% TODO: at the end of Section V, it is not fully clear what is best, what are the main benefits of the combination - it could be good to have a summary/recap sentence.
 
@@
 % Future work: ML for Rayleigh/Rician channels. Use in other fields like physics. Test with other KD functions. More models.
-We highlight in this work the benefits of incorporating theoretical models like maximum likelihood when training neural networks.
-We believe this is a crucial step to create networks that are more robust, which ensures higher trust in critical scenarios.
+We highlight in this work the benefits of incorporating additional information provided by theoretical models like maximum likelihood when training neural networks.
+We believe that this is a crucial step to create networks that are more robust, which ensures higher trust in critical scenarios.
 We showed that networks are more robust when distilling the probabilities given by these mathematical models, even when they operate under different priors.
 
-For future work, it could be interesting to explore other knowledge distillation losses and to use better ML functions that are adapted to Rayleigh or Rician channels, to improve the results when considering multiple types of channels.
+For future work, it could be interesting to explore other knowledge distillation losses and to use better ML functions that are adapted to Rayleigh or Rician channels, to improve the results in general cases that consider multiple types of channels.
 %Our methodology can also be explored in other research fields like physics, where neural networks are being increasingly preferred over mathematical models \pf{be a bit more precise, or skip this last part...}
